---
title: "Student Survey"
author: "Kelechi/Sidney"
date: "2025-02-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r}
# load packages #####
library(tidyverse)  # data processing
library(haven)      # read in stata data
library(vtable)     # summary tables
library(labelled)   # to see and create variable labels
library(sjPlot)    # regression tables
library(lme4)      # estimate MLM
library(lmerTest)  # hypothesis testing for MLM
library(quantreg)
library(blme)
library(writexl)
library(openxlsx)
library(ggplot2)
library(DescTools)
library(reshape2)

```

# Processing Survey Engagement

```{r}

data <- read.csv("survey_data_23_24.xlsx - survey data -- to share - Feb25_survey_data_23_24.xlsx - survey data.csv")

data$mid_year_math_relationship_average_rating <- as.numeric(data$mid_year_math_relationship_average_rating)

data$student_id <- data$Anon.Student.ID;
data$tutor_id <- data$Fellow.ID;

begin_vars <- colnames(data)[6:10];
mid_vars <- colnames(data)[11:16];
end_vars <- colnames(data)[17:22];

psych::alpha(data[begin_vars], na.rm = T)
psych::alpha(data[mid_vars], na.rm = T)
psych::alpha(data[end_vars], na.rm = T)

data$begin <- rowMeans(data[begin_vars], na.rm = T)
data$mid <- rowMeans(data[mid_vars], na.rm = T)
data$end <- rowMeans(data[end_vars], na.rm = T)


vars <- c("begin", "mid", "end");
psych::alpha(data[vars], na.rm = T)

data$engagement <- rowMeans(data[vars], na.rm = T)

tableone::CreateContTable(vars = vars, data = data);

data.melt <- melt(data[c(vars, "student_id", "tutor_id")], id = c("student_id", "tutor_id"))

m <- lmer(value ~ variable + (1 | student_id:tutor_id) + (1|tutor_id), data = data.melt)
tab_model(m)

emmeans::emmeans(m, pairwise ~ variable)

```

## Check for Duplicate in Enagement Survey

```{r}
# Check for duplicate 'student_id' in data df
duplicate_student_ids <- data %>% 
  group_by(Saga.Tutoring.ID) %>% 
  filter(n() > 1) %>% 
  ungroup()

# Print the duplicate student IDs
print(duplicate_student_ids)

```

# Individual Student-Tutor Modelling Approach

## Individual Student Data; Filtering

```{r}
seda_indvidual <- read.csv(file = "feb13_student_talkmove_achievement_merged.csv")

seda_mth_individual <- seda_indvidual

#Select Student_Tutor with achievement score
#seda_mth_individual <- seda_mth_individual %>% filter(is_in_achievement == 1)

#Select Student_Tutor with no multiple achievement score
#seda_mth_individual <- seda_mth_individual %>% filter(is_duplicated_student_tutor_x == 0)

# Select Student_Tutor with unique_session_IDs_count > 4
#seda_mth_individual <- seda_mth_individual %>% filter(unique_session_IDs_count >= 10)

# Select Student_Tutor with a tutor in the session
#seda_mth_individual <- seda_mth_individual %>% filter(unique_tutor_id_received_talkmove_count == 1)

dim(seda_mth_individual)
```

## Merge Survey and Talkmove

```{r}
#merge data df and seda_mth_individual
dim(seda_mth_individual)
merged_data_individual <- merge(seda_mth_individual, data, by.x = "student_id_utterance", by.y = "Saga.Tutoring.ID")
dim(merged_data_individual)

# Save merged_data as CSV
#write.csv(merged_data, "merged_data.csv", row.names = FALSE)


merged_data_individual <- merged_data_individual %>% filter(!is.nan(engagement))
dim(merged_data_individual)
```

## Column Renaming

```{r}
#Unweighted variables implies speaker level averaging
merged_data_individual <- merged_data_individual %>%
  mutate(
         student_talkmove_ratio = unweighted_student_talkmove_ratio,
         co_student_talkmove_ratio = unweighted_co_student_talkmove_ratio,
         student_utterance_ratio = unweighted_student_utterance_ratio,
         co_student_utterance_ratio = unweighted_co_student_utterance_ratio,
         tutor_talkmove_ratio = unweighted_tutor_talkmove_ratio,
         tutor_utterance_ratio = unweighted_tutor_utterance_ratio,
         student_relating_ratio = unweighted_student_relating_ratio,
         student_asking_for_info_ratio = unweighted_student_asking_for_info_ratio,
         student_making_claim_ratio = unweighted_student_making_claim_ratio,
         student_providing_evidence_ratio = unweighted_student_providing_evidence_ratio,
         Intercept = I,
         Slope = S,
         co_student_relating_ratio = unweighted_co_student_relating_ratio,
         co_student_asking_for_info_ratio = unweighted_co_student_asking_for_info_ratio,
         co_student_making_claim_ratio = unweighted_co_student_making_claim_ratio,
         co_student_providing_evidence_ratio = unweighted_co_student_providing_evidence_ratio,
         tutor_keeping_together = unweighted_tutor_keeping_together_ratio,
         tutor_students_relating = unweighted_tutor_students_relating_ratio,
         tutor_restating = unweighted_tutor_restating_ratio,
         tutor_revoicing = unweighted_tutor_revoicing_ratio,
         tutor_reasoning = unweighted_tutor_reasoning_ratio,
         
  )

```

## Winzeration of Predictor variables
```{r}
#Winsorize the variables

Vars <- c("student_talkmove_ratio", "co_student_talkmove_ratio", "tutor_talkmove_ratio", "student_utterance_ratio", "co_student_utterance_ratio", "tutor_utterance_ratio", "student_relating_ratio", "student_asking_for_info_ratio", "student_making_claim_ratio", "student_providing_evidence_ratio", "co_student_relating_ratio", "co_student_asking_for_info_ratio", "co_student_making_claim_ratio", "co_student_providing_evidence_ratio", "tutor_keeping_together", "tutor_students_relating", "tutor_restating", "tutor_revoicing", "tutor_reasoning")

for (var in Vars) {
  merged_data_individual[paste0(var, "_w")] <- (Winsorize(merged_data_individual[[var]], quantile(merged_data_individual[[var]], probs=c(0.0, 0.975), na.rm = FALSE)))
}
```



# MLM Modeling
## Talkmove by Speaker Type as Predictors

### Talkmove by student

```{r}
#Adding Individual Talkmove Predictors 30
model_240 <- blmer(engagement ~ student_talkmove_ratio_w +
              (1 + student_talkmove_ratio_w  | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

# Display the model summary
#tab_model(model_24)
```

```{r}
#Adding Individual Talkmove Predictors 30
model_241 <- blmer(engagement ~ co_student_talkmove_ratio_w +
              (1 + co_student_talkmove_ratio_w  | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```


```{r}
#Adding Individual Talkmove Predictors 30
model_242 <- blmer(engagement ~ tutor_talkmove_ratio_w +
              (1 | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
# Display the model summary
tab_model(model_240, model_241, model_242,  dv.labels = c("Student Talkmove", "Co Student Talkmove", "Tutor Talkmove"))
```

```{r}
#Adding Individual Talkmove Predictors 30
model_243 <- blmer(engagement ~ student_talkmove_ratio_w + co_student_talkmove_ratio_w + tutor_talkmove_ratio_w + tutor_utterance_ratio_w +
              (1 + student_talkmove_ratio_w + co_student_talkmove_ratio_w | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

# Display the model summary
tab_model(model_243)
```


## Model with interaction
```{r}
model_2430 <- blmer(engagement ~ student_talkmove_ratio_w*co_student_talkmove_ratio_w + student_talkmove_ratio_w*tutor_talkmove_ratio_w + tutor_utterance_ratio_w + (1 | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

# Display the model summary
tab_model(model_2430)
```




## Utterance by Speaker Type as Predictors

```{r}
model_340 <- blmer(engagement ~ student_utterance_ratio_w +
              (1 + student_utterance_ratio_w  | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

# Display the model summary
#tab_model(model_24)
```

```{r}
#Adding Individual Talkmove Predictors 30
model_341 <- blmer(engagement ~ co_student_utterance_ratio_w +
              (1 + co_student_utterance_ratio_w  | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 30
model_342 <- blmer(engagement ~ tutor_utterance_ratio_w +
              (1 | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
# Display the model summary
tab_model(model_340, model_341, model_342,  dv.labels = c("Student Utterance", "Co Student Utterance", "Tutor Utterance"))
```

```{r}
#Adding Individual Talkmove Predictors 30
model_343 <- blmer(engagement ~ student_utterance_ratio_w + co_student_utterance_ratio_w + tutor_utterance_ratio_w +
              (1 + student_utterance_ratio_w + co_student_utterance_ratio_w | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

# Display the model summary
tab_model(model_343)
```



## Talkmove Labels by Speaker Type as Predictors
### Talkmove by  Student

```{r}
#Adding Individual Talkmove Predictors 30
model_20 <- blmer(engagement ~ student_relating_ratio_w +
              (1 + student_relating_ratio_w | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
#Adding Individual Talkmove Predictors 31
model_21 <- blmer(engagement ~ student_asking_for_info_ratio_w +
              (1 + student_asking_for_info_ratio_w | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
#tab_model(model_21)

```

```{r}
#Adding Individual Talkmove Predictors 32
model_22 <- blmer(engagement ~ student_making_claim_ratio_w +
              (1 + student_making_claim_ratio_w | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_23 <- blmer(engagement ~ student_providing_evidence_ratio_w +
              (1 + student_providing_evidence_ratio_w | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
# Display the model summary
tab_model(model_20, model_21, model_22, model_23,  dv.labels = c("Student Relating", "Student Asking for Info", "Student making claim", "Student providing evidence"))
```


### Talkmove by Co student

```{r}
#Adding Individual Talkmove Predictors 30
model_020 <- blmer(engagement ~ co_student_relating_ratio_w +
              (1 + co_student_relating_ratio_w | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
#Adding Individual Talkmove Predictors 31
model_021 <- blmer(engagement ~ co_student_asking_for_info_ratio_w +
              (1 + co_student_asking_for_info_ratio_w | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
#tab_model(model_21)

```

```{r}
#Adding Individual Talkmove Predictors 32
model_022 <- blmer(engagement ~ co_student_making_claim_ratio_w +
              (1 + co_student_making_claim_ratio_w | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_023 <- blmer(engagement ~ co_student_providing_evidence_ratio_w +
              (1 + co_student_providing_evidence_ratio_w | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
# Display the model summary
tab_model(model_020, model_021, model_022, model_023,  dv.labels = c("Co Student Relating", "Co Student Asking for Info", "Co Student making claim", "Co Student providing evidence"))
```



### Talkmove by Tutor

```{r}
#Adding Individual Talkmove Predictors 30
model_420 <- blmer(engagement ~ tutor_keeping_together_w +
              (1 | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
#Adding Individual Talkmove Predictors 31
model_421 <- blmer(engagement ~ tutor_students_relating_w +
              (1 | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
#tab_model(model_21)

```

```{r}
#Adding Individual Talkmove Predictors 32
model_422 <- blmer(engagement ~ tutor_restating_w +
              (1 | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_423 <- blmer(engagement ~ tutor_revoicing_w +
              (1 | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_424 <- blmer(engagement ~ tutor_reasoning_w +
              (1 | tutor_id_utterance),
              data = merged_data_individual, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```



```{r}
# Display the model summary
tab_model(model_420, model_421, model_422, model_423, model_424,  dv.labels = c("Tutor Keeping Together", "Tutor Students Relating", "Tutor Restating", "Tutor Revoicing", "Tutor Reasoning"))
```




# Groups-of-Students attached to Tutor Approach

## Load Data and Filtering

```{r}
seda <- read.csv(file = "feb20_group_modelling_final_to_r_code.csv")

seda_mth <- seda

#Select Student_Tutor with achievement score
seda_mth <- seda_mth %>% filter(is_in_achievement == 1)

#Select Student_Tutor with no multiple achievement score
seda_mth <- seda_mth %>% filter(is_duplicated_student_tutor_x == 0)

# Select Student_Tutor with unique_session_IDs_count > 4
seda_mth <- seda_mth %>% filter(unique_session_IDs_count >= 10)

# Select Student_Tutor with a tutor in the session
seda_mth <- seda_mth %>% filter(unique_tutor_id_received_talkmove_count == 1)

dim(seda_mth)
```

## Column Renaming

```{r}
#Unweighted variables implies speaker level averaging
seda_mth <- seda_mth %>%
  mutate(
         student_group_talkmove_ratio = unweighted_student_talkmove_ratio,
         student_group_utterance_ratio = unweighted_student_utterance_ratio,
         tutor_talkmove_ratio = unweighted_tutor_talkmove_ratio,
         tutor_utterance_ratio = unweighted_tutor_utterance_ratio,
         student_group_relating_ratio = unweighted_student_relating_ratio,
         student_group_asking_for_info_ratio = unweighted_student_asking_for_info_ratio,
         student_group_making_claim_ratio = unweighted_student_making_claim_ratio,
         student_group_providing_evidence_ratio = unweighted_student_providing_evidence_ratio,
         Intercept = I,
         Slope = S,
         tutor_keeping_together = unweighted_tutor_keeping_together_ratio,
         tutor_students_relating = unweighted_tutor_students_relating_ratio,
         tutor_restating = unweighted_tutor_restating_ratio,
         tutor_revoicing = unweighted_tutor_revoicing_ratio,
         tutor_reasoning = unweighted_tutor_reasoning_ratio,
         
  )

```

## Merge Survey and Talkmove

```{r}
#merge data df and seda_mth
dim(seda_mth)
merged_data <- merge(seda_mth, data, by.x = "student_id_utterance", by.y = "Saga.Tutoring.ID")
dim(merged_data)

# Save merged_data as CSV
#write.csv(merged_data, "merged_data.csv", row.names = FALSE)


merged_data <- merged_data %>% filter(!is.nan(engagement))
dim(merged_data)
```

## Winzeration of Predictor variables
```{r}
#Winsorize the variables

Vars <- c("student_group_talkmove_ratio", "tutor_talkmove_ratio", "student_group_utterance_ratio", "tutor_utterance_ratio", "student_group_relating_ratio", "student_group_asking_for_info_ratio", "student_group_making_claim_ratio", "student_group_providing_evidence_ratio", "tutor_keeping_together", "tutor_students_relating", "tutor_restating", "tutor_revoicing", "tutor_reasoning")

for (var in Vars) {
  merged_data[paste0(var, "_w")] <- Winsorize(merged_data[[var]], quantile(merged_data[[var]], probs=c(0.0, 0.975), na.rm = FALSE))
}
```




# MLM Modeling
## Talkmove by Speaker Type as Predictors

```{r}
#Adding Individual Talkmove Predictors 30
model_84 <- blmer(engagement ~ student_group_talkmove_ratio_w +
              (1  | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 30
model_85 <- blmer(engagement ~ tutor_talkmove_ratio_w +
              (1  | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
# Display the model summary
tab_model(model_84, model_85,  dv.labels = c("Group Student Talkmove", "Tutor Talkmove"))
```

## Model with interaction
```{r}
model_12430 <- blmer(engagement ~ student_group_talkmove_ratio_w*tutor_talkmove_ratio_w + tutor_utterance_ratio_w + (1 | tutor_id_utterance),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

# Display the model summary
tab_model(model_12430)
```




```{r}
#Adding Individual Talkmove Predictors 30
model_86 <- blmer(engagement ~ student_group_talkmove_ratio_w + tutor_talkmove_ratio_w +
              (1  | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
tab_model(model_86)
```




## Utterance Ratio by Speaker Type as Predictors

```{r}
#Adding Individual Talkmove Predictors 31
model_87 <- blmer(engagement ~ student_group_utterance_ratio_w +
              (1 | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
#Adding Individual Talkmove Predictors 32
model_88 <- blmer(engagement ~ tutor_utterance_ratio_w +
              (1 | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
# Display the model summary
tab_model(model_87, model_88,  dv.labels = c("Group Student Utterance", "Tutor Utterance"))
```

```{r}
#Adding Individual Talkmove Predictors 33
model_89 <- blmer(engagement ~ student_group_utterance_ratio_w + tutor_utterance_ratio_w +
              (1 | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
tab_model(model_89)
```




## Talkmove Labels by Speaker Type as Predictors
### Talkmove by  Student

```{r}
#Adding Individual Talkmove Predictors 30
model_80 <- blmer(engagement ~ student_group_relating_ratio_w +
              (1  | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 31
model_81 <- blmer(engagement ~ student_group_asking_for_info_ratio_w +
              (1 | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_82 <- blmer(engagement ~ student_group_making_claim_ratio_w +
              (1 | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_83 <- blmer(engagement ~ student_group_providing_evidence_ratio_w +
              (1 | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
# Display the model summary
tab_model(model_80, model_81, model_82, model_83,  dv.labels = c("Student Relating", "Student Asking for Info", "Student making claim", "Student providing evidence"))
```

### Talkmove by Tutor
```{r}
#Adding Individual Talkmove Predictors 30
model_40 <- blmer(engagement ~ tutor_keeping_together_w +
              (1 | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
#Adding Individual Talkmove Predictors 31
model_41 <- blmer(engagement ~ tutor_students_relating_w +
              (1 | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
#Adding Individual Talkmove Predictors 32
model_42 <- blmer(engagement ~ tutor_restating_w +
              (1 | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
#Adding Individual Talkmove Predictors 32
model_43 <- blmer(engagement ~ tutor_revoicing_w +
              (1 | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
#Adding Individual Talkmove Predictors 32
model_44 <- blmer(engagement ~ tutor_reasoning_w +
              (1 | student_tutor_group),
              data = merged_data, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
# Display the model summary
tab_model(model_40, model_41, model_42, model_43, model_44,  dv.labels = c("Tutor Keeping Together", "Tutor Students Relating", "Tutor Restating", "Tutor Revoicing", "Tutor Reasoning"))
```

