---
title: "Descriptive Analysis of SEDA 2022 + Datahub Data"
author: "Benjamin Shear"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r}
# load packages #####
library(tidyverse)  # data processing
library(haven)      # read in stata data
library(vtable)     # summary tables
library(labelled)   # to see and create variable labels
library(lme4)      # estimate MLM
library(sjPlot)    # regression tables
library(lme4)      # estimate MLM
library(lmerTest)  # hypothesis testing for MLM
library(tidyverse) # data management
library(quantreg)
library(blme)

```

## Overview

This file will create descriptive statistics of the final sample. The raw data sources and key variables are:

- [Stanford Education Data Archive](https://edopportunity.org) for data about student achievement. The key variable of interest is the change in average test scores from spring 2019 to spring 2022, in math and in reading/language arts (RLA).

- [Datahub](https://www.covidschooldatahub.com) for data about the proportion of the year each school district had students learning in person versus in hybrid or virtual formats.

## Load Data

```{r}
seda <- read.csv(file = "processed_summary_of_speaker-utterances3.csv")
```

## Limit to Math scores

For the moment, let's analyze just math data and leave aside RLA.

```{r}
dim(seda)
#seda_mth <- filter(seda, relationship_with_tutor_check=="TRUE")
#table(seda_mth$relationship_with_tutor_check, useNA="a")
```
## Data Filterering

```{r}
# Drop rows with any missing data
seda_mth <- seda %>% drop_na()


# Drop cases where coach_ID_y is not equal to coach_ID_x
seda_mth <- seda_mth %>% filter(coach_ID_y == coach_ID_x)

# Drop cases where unique_student_id_received_talkmove_count > 4
seda_mth <- seda_mth %>% filter(unique_student_id_received_talkmove_count <= 4)


# Drop cases where unique_session_IDs_count > 4
seda_mth <- seda_mth %>% filter(unique_session_IDs_count >= 4)
dim(seda_mth)
```


## Full Sample Descriptives

```{r}
sumtable(seda_mth)
```


## Level 1 Descriptives

```{r}
#seda_mth$average_talkmove_ratio <- round(seda_mth$average_talkmove_ratio, 8)
#seda_mth$average_received_student_talkmove <- round(seda_mth$average_received_student_talkmove, 8)
#seda_mth$average_received_tutor_talkmove <- round(seda_mth$average_received_tutor_talkmove, 8)
#seda_mth$Initial_score <- round(seda_mth$Initial_score, 8)
#seda_mth$Final_score <- round(seda_mth$Final_score, 8)
#sumtable(seda_mth,
#         vars = c("student_ID", "average_talkmove_ratio", "average_received_student_talkmove",
#                  "Initial_score", "Final_score", "region"),
#         digits=2)



seda_mth %>%
  select(average_talkmove_ratio, average_received_student_talkmove, Slope, Initial_score, relationship_with_tutor, unique_session_IDs_count) %>%
  sumtable()
```

### Adjust the statistics included

Let's report only the N, mean, SD, min, and max.

```{r}
sumtable(seda_mth,
         vars = c("average_talkmove_ratio", "average_received_student_talkmove", "Initial_score", "Final_score", "region"),
         digits=2,
         summ = c('notNA(x)','mean(x)','sd(x)','min(x)','max(x)'))
```

## Level 2 Descriptives

```{r}
lev2 <- seda_mth %>%
  group_by(tutor_ID) %>%
  summarise(
    NDist=n(),
    Mean_teacher_eff=mean(average_received_tutor_talkmove)
  ) %>%
  ungroup()
```

```{r}
sumtable(lev2, digits=2)
```


```{r}
seda_mth %>%
  group_by(tutor_ID, coach_ID_y) %>%
  summarise(
    Mean_teacher_eff=mean(average_received_tutor_talkmove),
    N_Tutors=n(),
  ) %>%
  ungroup() %>%
  select(-tutor_ID, coach_ID_y) %>%
  sumtable()
```


## Level 3 Descriptives

```{r}
lev3 <- seda_mth %>%
  group_by(coach_ID_y) %>%
  summarise(
    assigned_unique_tutors = n_distinct(tutor_ID),  # Count unique tutors assigned to each coach
    NDist=n(),
    .groups = "drop"
  )
```

```{r}
sumtable(lev3, digits=2)
```



```{r}
## level 3 (hospitals) -----

seda_mth %>%
  group_by(coach_ID_y) %>%
  summarise(
    N_coaches=n(),
    assigned_unique_tutors = n_distinct(tutor_ID),  # Count unique tutors assigned to each coach %>%
  )
  ungroup() %>%
  select(-coach_ID_y) %>%
  sumtable()
```

### Adjust the statistics included

For consistency, we could limit to the same statistics as Level 1 above:

```{r}
sumtable(lev2,
         digits=2,
         summ = c('notNA(x)','mean(x)','sd(x)','min(x)','max(x)'))
```

## Histograms

Histogram Final Math for each Student.

```{r}
ggplot(aes(x=Final_score), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram Student Final Maths score after the 3rd round of assessement") +
  ylab("Count") +
  theme_bw() 
```
## Histograms

Histogram of Slope for each Student.

```{r}
ggplot(aes(x=Slope), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Student's Slope of maths scores") +
  ylab("Count") +
  theme_bw() 
```




Histogram of percent of time in person across districts.

```{r}
ggplot(aes(x=average_talkmove_ratio), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram Talkmove Ratio for each Student") +
  ylab("Count") +
  theme_bw() 
```

Tutors average talkmove usage.

```{r}
ggplot(aes(x=Mean_teacher_eff), data = lev2) +
  geom_histogram(fill="grey",color="black", bins=10) +
  xlab("Tutors average talkmove usage") +
  ylab("Count") +
  theme_bw() 
```

## Scatterplots

Show the association between share in person and change in math scores pooling across all states, and save as a png file.

```{r}
seda_mth %>%
  ggplot(aes(x=average_talkmove_ratio, y=Final_score)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Final Maths Score") +
  xlab("Student's average usage of talkmoves") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)
```

```{r}
cor(seda_mth$average_talkmove_ratio, seda_mth$Final_score)
mod1 <- rq(Final_score ~ average_talkmove_ratio, data = seda_mth, tau = c(0.25, 0.5, 0.75))
summary(mod1)

# mod1 <- lm(Final_score ~ average_talkmove_ratio, data = seda_mth)
# summary(mod1)

plot(seda_mth$average_talkmove_ratio, seda_mth$Final_score)
abline(0.61772 , 0.29171 , lwd = 2, col = rgb(0,0,0,.5))

abline(0.62744, 0.31926 , lwd = 2, col = rgb(0,1,0,.5))
abline(0.43593, 0.43593, lwd = 2, col = rgb(1,0,0,.5))
abline(0.80722, 0.11142, lwd = 2, col = rgb(0,0,1,.5))

```


```{r}
seda_mth %>%
  ggplot(aes(x=average_talkmove_ratio, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Maths score Slope") +
  xlab("Student's average usage of talkmoves") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)

```



Now we can look at the association separately for each state.

```{r}
tutor_group <- seda_mth %>%
  group_by(tutor_ID) %>%  # Group by tutor_ID
  select(tutor_ID,  # Keep tutor_ID in the selection
         average_talkmove_ratio, 
         Slope, 
         Initial_score, 
         baseline_math_efficancy_survey, 
         Final_score)  # Select the relevant columns



# Sample 10 random tutors
sampled_tutors <- tutor_group %>%
  ungroup() %>%  # Remove any grouping
  distinct(tutor_ID) %>%  # Get distinct tutor_IDs
  sample_n(20)  # Sample 10 random tutors

# Filter the original dataset to include only the sampled tutors
seda_mth_sampled <- seda_mth %>%
  filter(tutor_ID %in% sampled_tutors$tutor_ID)
```


```{r, fig.height=6, fig.width=13}
# Plot for the sampled students
seda_mth_sampled %>%
  ggplot(aes(x=average_talkmove_ratio, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +  # Scatter points
  geom_smooth(method="lm", se=FALSE, color="blue") +  # Linear regression line
  facet_wrap(~tutor_ID, nrow=3) +  # Facet by student
  ylab("Student Maths Slope") + 
  xlab("Student's Average Usage of Talkmoves") + 
  theme_bw(base_size=10) +  # Theme for better visualization
  theme(strip.text = element_text(size = 8))  # Adjust size of facet labels for clarity

ggsave(filename="statescatters_random10.png", height=6, width=13)
```

```{r}
model1 = blmer(Slope ~ 1 + (1 | tutor_ID), data = seda_mth, REML = FALSE)

tab_model(model1, dv.labels = c("Tutor Null Model"))
```





```{r}
model2 <- lmer(Slope ~ 1 + (1 | tutor_ID) + (1 | tutor_ID:coach_ID_y), data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

# Display the model summary
tab_model(model2, dv.labels = c("Coach Null Model"))
```







```{r}
#Empty Model
model1 = lmer(Slope ~ 1 + Initial_score +  (1 | tutor_ID), data = seda_mth, REML = FALSE)

tab_model(model1, dv.labels = c("Tutor Random Intercept Model"))
```



```{r}
#Adding Talkmove Predictors

model3 <- blmer(Slope ~ 1 + average_talkmove_ratio + Initial_score + average_received_tutor_talkmove  + 
              (1 + average_talkmove_ratio +  Initial_score | tutor_ID) + 
              (1 + average_talkmove_ratio +  Initial_score + average_received_tutor_talkmove| coach_ID_y:tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

tab_model(model3, dv.labels = c("Tutor-Coach Random Intercept Model"))

```


```{r}

#Interaction of student talk and student_relationship_with_tutor

model4 <- blmer(Slope ~ 1 + average_talkmove_ratio + Initial_score + average_received_tutor_talkmove  + relationship_with_tutor + average_talkmove_ratio:relationship_with_tutor +
              (1 + average_talkmove_ratio +  Initial_score + average_received_tutor_talkmove + relationship_with_tutor + average_talkmove_ratio:relationship_with_tutor| tutor_ID) + 
              (1 + average_talkmove_ratio +  Initial_score + average_received_tutor_talkmove + relationship_with_tutor + average_talkmove_ratio:relationship_with_tutor | coach_ID_y:tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

tab_model(model4, dv.labels = c("Interation Model"))
```
**Create plots to assess the normality of the level-1 and level-2 residuals. Does assuming normality seem reasonable for these data?**

```{r}
level1_residual <- resid(model3)

#head(level1_residual)
hist(level1_residual, main="Level-1 Residuals Histogram Plot")
#qqline(level1_residual, col="red")


level2_residual <- ranef(model3)$tutor_ID
#head(level2_residual)
hist(level2_residual$average_received_tutor_talkmove , main="Level-2 time Residuals Histogram Plot")
#qqline(level2_residual$time, col="red")

hist(level2_residual$`(Intercept)`, main="Level-2 Intercept Residuals Histogram Plot")
#qqline(level2_residual$`(Intercept)`, col="red")
```

- From the level-1 and level-2 residual histograms, we could see that residuals are not perfectly normal, however, we could approximately agree that they have the shape of a normal distribution.

