---
title: "Analysis of Talk Move Dataset"
author: "Kelechi Ezema"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r}
# load packages #####
library(tidyverse)  # data processing
library(haven)      # read in stata data
library(vtable)     # summary tables
library(labelled)   # to see and create variable labels
library(lme4)      # estimate MLM
library(sjPlot)    # regression tables
library(lme4)      # estimate MLM
library(lmerTest)  # hypothesis testing for MLM
library(tidyverse) # data management
library(quantreg)
library(blme)
library(writexl)
library(openxlsx)

```


## Load Data

```{r}
seda <- read.csv(file = "student_talkmove_summary_with_dorminat_details_file_merged.csv")
```



## Data Filterering

```{r}
seda_mth <- seda


# Drop students not found in achievement_data
seda_mth <- seda_mth %>% filter(found_in_achievement_data == 1)

# Drop students not found in saga_crosswalk_data
#seda_mth <- seda_mth %>% filter(found_in_saga_crosswalk == 1)

# Drop students not found in survey_data
#seda_mth <- seda_mth %>% filter(found_in_survey_main == 1)


# Drop students with no dominate tutor_id
seda_mth <- seda_mth %>% filter(!is.na(dominate_tutor_id))

# Drop students with no dominate coach_id
seda_mth <- seda_mth %>% filter(!is.na(dominant_coach_id))

# Drop cases where unique_session_IDs_count > 4
#seda_mth <- seda_mth %>% filter(unique_session_IDs_count >= 4)
dim(seda_mth)
```
```{r}
#Multiply Talkmoves per session
seda_mth <- seda_mth %>%
  mutate(average_talkmove_ratio = average_talkmove_ratio * unique_session_IDs_count,
         average_received_student_talkmove = average_received_student_talkmove * unique_session_IDs_count,
         average_received_tutor_talkmove = average_received_tutor_talkmove * unique_session_IDs_count,
         Slope = Slope *100,
         Intercept = Intercept*100
         
  )

```


## Full Sample Descriptives

```{r}
sumtable(seda_mth)
```


## Level 1 Descriptives

```{r}
# Get the summary and store it in a variable
summary_table <- seda_mth %>%
  select(average_talkmove_ratio, average_received_student_talkmove, Slope, Intercept, unique_session_IDs_count) %>%
  sumtable()
```


## Level 2 Descriptives

```{r}
lev2 <- seda_mth %>%
  group_by(dominate_tutor_id) %>%
  summarise(
    Assigned_unique_student=n(),
    Mean_tutor_talkmove=mean(average_received_tutor_talkmove)
  ) %>%
  ungroup() %>%
  select(-dominate_tutor_id)
```

```{r}
sumtable(lev2, digits=2)
```


## Level 3 Descriptives

```{r}
lev3 <- seda_mth %>%
  group_by(dominant_coach_id) %>%
  summarise(
    assigned_unique_tutors = n_distinct(dominate_tutor_id),  # Count unique tutors assigned to each coach
    Assigned_unique_student=n(), # Count unique student assigned to each coach
    ) %>%
  ungroup() %>%
  select(-dominant_coach_id)
```

```{r}
sumtable(lev3, digits=2)
```





## Histograms

Histogram of Slope for each Student Maths score slope.

```{r}
ggplot(aes(x=Slope), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Student's Slope of maths scores") +
  ylab("Count") +
  theme_bw() 
```



Histogram of Intercept for each Student Maths score slope.

```{r}
ggplot(aes(x=Intercept), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Student's Intercept of maths scores") +
  ylab("Count") +
  theme_bw() 
```




Histogram of Student's Talkmove Ratio.

```{r}
ggplot(aes(x=average_talkmove_ratio), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram Talkmove Ratio for each Student") +
  ylab("Count") +
  theme_bw() 
```







## Scatterplots
Now we can look at the association Talkmove and learning gain for each student


```{r}
seda_mth %>%
  ggplot(aes(x=average_talkmove_ratio, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Maths score Slope") +
  xlab("Student's usage of talkmoves") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)
```


```{r}
seda_mth %>%
  ggplot(aes(x=average_received_student_talkmove, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Maths score Slope") +
  xlab("Co Student's usage of talkmoves") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)
```

```{r}
seda_mth %>%
  ggplot(aes(x=average_received_tutor_talkmove, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Maths score Slope") +
  xlab("Assigned tutor usage of talkmoves") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)
```

```{r}
tutor_group <- seda_mth %>%
  group_by(dominate_tutor_id) %>%  # Group by dominate_tutor_id
  select(dominate_tutor_id,  # Keep dominate_tutor_id in the selection
         average_talkmove_ratio, 
         Slope, 
         Intercept, 
         )  # Select the relevant columns



# Sample 10 random tutors
sampled_tutors <- tutor_group %>%
  ungroup() %>%  # Remove any grouping
  distinct(dominate_tutor_id) %>%  # Get distinct tutor_IDs
  sample_n(20)  # Sample 10 random tutors

# Filter the original dataset to include only the sampled tutors
seda_mth_sampled <- seda_mth %>%
  filter(dominate_tutor_id %in% sampled_tutors$dominate_tutor_id)
```
 

```{r, fig.height=6, fig.width=13}
# Plot for the sampled students
seda_mth_sampled %>%
  ggplot(aes(x=average_talkmove_ratio, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +  # Scatter points
  geom_smooth(method="lm", se=FALSE, color="blue") +  # Linear regression line
  facet_wrap(~dominate_tutor_id, nrow=3) +  # Facet by student
  ylab("Student Maths Slope") + 
  xlab("Student's Average Usage of Talkmoves") + 
  theme_bw(base_size=10) +  # Theme for better visualization
  theme(strip.text = element_text(size = 8))  # Adjust size of facet labels for clarity

ggsave(filename="statescatters_random10.png", height=6, width=13)
```
#Corrlation of talkmoves
```{r}
# Select relevant variables
data <- seda_mth[, c("average_talkmove_ratio",	"average_received_student_talkmove", "average_received_tutor_talkmove")]  


# Check new dimensions of the dataset
dim(data)  # Returns number of rows and columns

#Calculate a correlation matrix
cor_matrix <- cor(data)

# Convert the correlation matrix to a dataframe
cor_df <- as.data.frame(cor_matrix)

#write.csv(cor_df, "correlation_matrix.csv")

#Print
print(cor_matrix)
```




## Empty Intercepts and Random Intercept MLM Models 
```{r}
#Empty Intercept Model
model2 <- blmer(Slope ~ 1 + (1 | dominate_tutor_id) + (1 | dominate_tutor_id:dominant_coach_id), data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
tab_model(model2)

```
```{r}
#Adding Talkmove Predictors 01
model_01 <- blmer(Slope ~ 1 + average_talkmove_ratio +
              (1 + average_talkmove_ratio | dominate_tutor_id) + 
              (1 + average_talkmove_ratio | dominant_coach_id:dominate_tutor_id),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
# Display the model summary
tab_model(model_01)

```
  
  
  
  
```{r}
#Adding Talkmove Predictors 02
model_02 <- blmer(Slope ~ 1 + average_received_student_talkmove +
              (1 + average_received_student_talkmove | dominate_tutor_id) + 
              (1 + average_received_student_talkmove | dominant_coach_id:dominate_tutor_id),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
# Display the model summary
tab_model(model_02)
```
  
```{r}
#Adding Talkmove Predictors 03
model_03 <- blmer(Slope ~ 1 + average_received_tutor_talkmove +
              (1 | dominate_tutor_id) + 
              (1 | dominant_coach_id:dominate_tutor_id),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
# Display the model summary
tab_model(model_03)
```
```{r}
# Display the model summary
tab_model(model2, model_01, model_02, model_03,  dv.labels = c("Null Model", "Student TalkMove", "Co student Talkmove", "Tutor Talkmove"))
```
  
  
  
  
  
  
  
  
```{r}
#Adding Talkmove Predictors
model4 <- blmer(Slope ~ 1 + average_talkmove_ratio + average_received_student_talkmove + average_received_tutor_talkmove  +
              (1 + average_talkmove_ratio + average_received_student_talkmove | dominate_tutor_id) + 
              (1 + average_talkmove_ratio + average_received_student_talkmove | dominant_coach_id:dominate_tutor_id),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```


```{r}

# Display the model summary
tab_model(model2, model4,  dv.labels = c("Null Model", "TalkMove Model"))

```

```{r}
#Adding Talkmove, Intercept and attendance
model5 <- blmer(Slope ~ 1 + Intercept + unique_session_IDs_count + average_talkmove_ratio + average_received_student_talkmove + average_received_tutor_talkmove  +
              (1 + Intercept + unique_session_IDs_count + average_talkmove_ratio + average_received_student_talkmove | dominate_tutor_id) + 
              (1 + Intercept + unique_session_IDs_count + average_talkmove_ratio + average_received_student_talkmove | dominant_coach_id:dominate_tutor_id),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

# Display the model summary
tab_model(model5)

```



## Plots to assess the normality of the residuals.
```{r}
# Extract residuals and random effects
residuals <- resid(model4)
ranef_tutor <- ranef(model4)$tutor_ID
ranef_coach <- ranef(model4)$`coach_ID_y:tutor_ID`

# Create Q-Q plot for level-1 residuals
qqnorm(residuals, main="Q-Q Plot of Level-1 Residuals")
qqline(residuals, col="red")

# Create Q-Q plots for level-2 random effects (tutor level)
qqnorm(ranef_tutor$`(Intercept)`, main="Q-Q Plot of Tutor-Level Random Intercepts")
qqline(ranef_tutor$`(Intercept)`, col="red")



# Create Q-Q plots for level-3 random effects (coach level)
qqnorm(ranef_coach$`(Intercept)`, main="Q-Q Plot of Coach-Level Random Intercepts")
qqline(ranef_coach$`(Intercept)`, col="red")

```


