---
title: "Analysis of Talk Move Dataset"
author: "Kelechi Ezema"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r}
# load packages #####
library(tidyverse)  # data processing
library(haven)      # read in stata data
library(vtable)     # summary tables
library(labelled)   # to see and create variable labels
library(lme4)      # estimate MLM
library(sjPlot)    # regression tables
library(lme4)      # estimate MLM
library(lmerTest)  # hypothesis testing for MLM
library(tidyverse) # data management
library(quantreg)
library(blme)
library(writexl)
library(openxlsx)

```


## Load Data

```{r}
seda <- read.csv(file = "processed_summary_of_speaker-utterances3.csv")
```



## Data Filterering

```{r}
# Drop rows with any missing data
seda_mth <- seda %>% drop_na()


# Drop cases where coach_ID_y is not equal to coach_ID_x
seda_mth <- seda_mth %>% filter(coach_ID_y == coach_ID_x)

# Drop cases where unique_student_id_received_talkmove_count > 4
seda_mth <- seda_mth %>% filter(unique_student_id_received_talkmove_count <= 4)


# Drop cases where unique_session_IDs_count > 4
seda_mth <- seda_mth %>% filter(unique_session_IDs_count >= 4)
dim(seda_mth)
```


## Full Sample Descriptives

```{r}
sumtable(seda_mth)
```


## Level 1 Descriptives

```{r}
# Get the summary and store it in a variable
summary_table <- seda_mth %>%
  select(average_talkmove_ratio, average_received_student_talkmove, Slope, Initial_score, relationship_with_tutor, unique_session_IDs_count) %>%
  sumtable()
```


## Level 2 Descriptives

```{r}
lev2 <- seda_mth %>%
  group_by(tutor_ID) %>%
  summarise(
    NDist=n(),
    Mean_teacher_eff=mean(average_received_tutor_talkmove)
  ) %>%
  ungroup()
```

```{r}
sumtable(lev2, digits=2)
```


## Level 3 Descriptives

```{r}
lev3 <- seda_mth %>%
  group_by(coach_ID_y) %>%
  summarise(
    assigned_unique_tutors = n_distinct(tutor_ID),  # Count unique tutors assigned to each coach
    NDist=n(),
    .groups = "drop"
  )
```

```{r}
sumtable(lev3, digits=2)
```





## Histograms

Histogram of Slope for each Student Maths score slope.

```{r}
ggplot(aes(x=Slope), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Student's Slope of maths scores") +
  ylab("Count") +
  theme_bw() 
```




Histogram of Student's Talkmove Ratio.

```{r}
ggplot(aes(x=average_talkmove_ratio), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram Talkmove Ratio for each Student") +
  ylab("Count") +
  theme_bw() 
```

## Scatterplots

Now we can look at the association Talkmove and learning gain for each student

```{r}
tutor_group <- seda_mth %>%
  group_by(tutor_ID) %>%  # Group by tutor_ID
  select(tutor_ID,  # Keep tutor_ID in the selection
         average_talkmove_ratio, 
         Slope, 
         Initial_score, 
         baseline_math_efficancy_survey, 
         Final_score)  # Select the relevant columns



# Sample 10 random tutors
sampled_tutors <- tutor_group %>%
  ungroup() %>%  # Remove any grouping
  distinct(tutor_ID) %>%  # Get distinct tutor_IDs
  sample_n(20)  # Sample 10 random tutors

# Filter the original dataset to include only the sampled tutors
seda_mth_sampled <- seda_mth %>%
  filter(tutor_ID %in% sampled_tutors$tutor_ID)
```
 

```{r, fig.height=6, fig.width=13}
# Plot for the sampled students
seda_mth_sampled %>%
  ggplot(aes(x=average_talkmove_ratio, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +  # Scatter points
  geom_smooth(method="lm", se=FALSE, color="blue") +  # Linear regression line
  facet_wrap(~tutor_ID, nrow=3) +  # Facet by student
  ylab("Student Maths Slope") + 
  xlab("Student's Average Usage of Talkmoves") + 
  theme_bw(base_size=10) +  # Theme for better visualization
  theme(strip.text = element_text(size = 8))  # Adjust size of facet labels for clarity

ggsave(filename="statescatters_random10.png", height=6, width=13)
```




## Empty Intercepts and Random Intercept MLM Models 
```{r}
#Empty Intercept Model
model2 <- lmer(Slope ~ 1 + (1 | tutor_ID) + (1 | tutor_ID:coach_ID_y), data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```


```{r}
#Adding Talkmove Predictors
model4 <- blmer(Slope ~ 1 + average_talkmove_ratio + average_received_student_talkmove + average_received_tutor_talkmove  +
              (1 + average_talkmove_ratio + average_received_student_talkmove | tutor_ID) + 
              (1 + average_talkmove_ratio + average_received_student_talkmove | coach_ID_y:tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```


```{r}

# Display the model summary
tab_model(model2, model4,  dv.labels = c("Null Model", "TalkMove Model"))

```




## Plots to assess the normality of the residuals.
```{r}
# Extract residuals and random effects
residuals <- resid(model4)
ranef_tutor <- ranef(model4)$tutor_ID
ranef_coach <- ranef(model4)$`coach_ID_y:tutor_ID`

# Create Q-Q plot for level-1 residuals
qqnorm(residuals, main="Q-Q Plot of Level-1 Residuals")
qqline(residuals, col="red")

# Create Q-Q plots for level-2 random effects (tutor level)
qqnorm(ranef_tutor$`(Intercept)`, main="Q-Q Plot of Tutor-Level Random Intercepts")
qqline(ranef_tutor$`(Intercept)`, col="red")



# Create Q-Q plots for level-3 random effects (coach level)
qqnorm(ranef_coach$`(Intercept)`, main="Q-Q Plot of Coach-Level Random Intercepts")
qqline(ranef_coach$`(Intercept)`, col="red")

```


