---
title: "Student Engagmement"
author: "Kelechi Ezema"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r}
# load packages #####
library(tidyverse)  # data processing
library(haven)      # read in stata data
library(vtable)     # summary tables
library(labelled)   # to see and create variable labels
library(lme4)      # estimate MLM
library(sjPlot)    # regression tables
library(lmerTest)  # hypothesis testing for MLM
library(quantreg)
library(blme)
library(writexl)
library(openxlsx)
library(robustlmm)
library(DescTools)
library(reshape2)
library(robustlmm)
library(visreg)
library(emmeans)
library(car)

```


## Load Data

```{r}
seda <- read.csv(file = "march_14_group_modelling_student_talkmove_achievement_survey_merged.csv")
#seda <- read.csv(file = "march_19_group_modelling_student_talkmove_old_achievement_survey_merged.csv")

```



## Data Filterering

```{r}
seda_mth <- seda

#Select Student_Tutor with achievement score
seda_mth <- seda_mth %>% filter(is_in_achievement == 1)

#Select Student_Tutor with no multiple achievement score
seda_mth <- seda_mth %>% filter(is_duplicated_student_tutor_x == 0)

# Select Student_Tutor with unique_session_IDs_count > 10
seda_mth <- seda_mth %>% filter(unique_session_IDs_count >= 10)

# Select Student_Tutor with a tutor in the session
seda_mth <- seda_mth %>% filter(unique_tutor_id_received_talkmove_count == 1)

dim(seda_mth)
```
## Group Talk and Student Talk Adjustment

```{r eval=FALSE, include=FALSE}
# Group by student_tutor_group, calculate group_slope, and then calculate diff_group_slope
#seda_mth <- seda_mth %>%
#  group_by(student_tutor_group) %>%
#  mutate(group_slope = mean(S, na.rm = TRUE),
#         group_intercept = mean(I, na.rm = TRUE),
#         diff_group_slope = S - group_slope,
#         diff_group_intercept = I - group_intercept,
#         ) %>%
#  ungroup()

```




## Column Renaming

```{r}
#Unweighted variables implies speaker level averaging
seda_mth <- seda_mth %>%
  mutate(
         student_group_talkmove_ratio = unweighted_student_talkmove_ratio,
         student_group_utterance_ratio = unweighted_student_utterance_ratio,
         tutor_talkmove_ratio = unweighted_tutor_talkmove_ratio,
         tutor_utterance_ratio = unweighted_tutor_utterance_ratio,
         student_group_relating_ratio = unweighted_student_relating_ratio,
         student_group_asking_for_info_ratio = unweighted_student_asking_for_info_ratio,
         student_group_making_claim_ratio = unweighted_student_making_claim_ratio,
         student_group_providing_evidence_ratio = unweighted_student_providing_evidence_ratio,
         Intercept = I,
         Slope = S,
         tutor_keeping_together = unweighted_tutor_keeping_together_ratio,
         tutor_students_relating = unweighted_tutor_students_relating_ratio,
         tutor_restating = unweighted_tutor_restating_ratio,
         tutor_revoicing = unweighted_tutor_revoicing_ratio,
         tutor_reasoning = unweighted_tutor_reasoning_ratio,
  )

```

## Winzeration of Predictor variables
```{r}
#Winsorize the variables

Vars <- c("student_group_talkmove_ratio", "tutor_talkmove_ratio", "student_group_utterance_ratio", "tutor_utterance_ratio", "student_group_relating_ratio", "student_group_asking_for_info_ratio", "student_group_making_claim_ratio", "student_group_providing_evidence_ratio", "tutor_keeping_together", "tutor_students_relating", "tutor_restating", "tutor_revoicing", "tutor_reasoning")

for (var in Vars) {
  seda_mth[paste0(var, "_w")] <- Winsorize(seda_mth[[var]], quantile(seda_mth[[var]], probs=c(0.0, 0.99), na.rm = FALSE))
}
```




## Rescaling Achievement Intercept and Slope

```{r}
seda_mth <- seda_mth %>%
  mutate(
         Slope = Slope *100,
         Intercept = Intercept*100
  )

```


## Level 1 Descriptives

```{r}
# Get the summary and store it in a variable
lev1 <- seda_mth %>%
  select(Slope, Intercept, unique_session_IDs_count)
  sumtable(lev1)
```


## Level 2 Descriptives

```{r}
lev2 <- seda_mth %>%
  group_by(student_tutor_group) %>%
  summarise(
    
    #Assigned_unique_student=n(),
    participant_count = mean(participant_count),
    Mean_tutor_talkmove=mean(tutor_talkmove_ratio_w),
    Mean_tutor_utterance=mean(tutor_utterance_ratio_w),
    Mean_student_group_talkmove=mean(student_group_talkmove_ratio_w),
    Mean_student_group_uttera=mean(student_group_utterance_ratio_w)
  ) %>%
  ungroup() %>%
  select(-student_tutor_group)
sumtable(lev2, digits=2)
```



## Histograms

```{r}
ggplot(aes(x=Slope), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Student's Slope of maths scores") +
  ylab("Count") +
  theme_bw() 
```



```{r}
ggplot(aes(x=Intercept), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Student's Intercept of maths scores") +
  ylab("Count") +
  theme_bw() 
```




## Talkmove Histogram for speaker type

```{r}
ggplot(aes(x=student_group_talkmove_ratio_w), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Student's Group Proportion of Talkmove") +
  ylab("Count") +
  theme_bw() 
```

```{r}
ggplot(aes(x=tutor_talkmove_ratio_w), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Tutor's Proportion of Talkmove") +
  ylab("Count") +
  theme_bw() 
```

## Utterance Histogram for speaker type
```{r}
ggplot(aes(x=student_group_utterance_ratio_w), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Student's Group Utterance Proportion") +
  ylab("Count") +
  theme_bw() 
```


```{r}
ggplot(aes(x=tutor_utterance_ratio_w), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Tutor's Utterance Proportion") +
  ylab("Count") +
  theme_bw() 
```



## Speaker's Talkmove Scattarplot

```{r}
seda_mth %>%
  ggplot(aes(x=student_group_talkmove_ratio_w, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Maths score Slope") +
  xlab("Student's Group talkmoves proportion") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)
```

```{r}
seda_mth %>%
  ggplot(aes(x=tutor_talkmove_ratio_w, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Maths score Slope") +
  xlab("Tutor's talkmoves proportion") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)
```


## Speaker's Utterance Scatterplots

```{r}
seda_mth %>%
  ggplot(aes(x=student_group_utterance_ratio_w, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Maths score Slope") +
  xlab("Student's Group utterance proportion") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)
```



```{r}
seda_mth %>%
  ggplot(aes(x=tutor_utterance_ratio_w, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Maths score Slope") +
  xlab("Tutor utterance proportion") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)
```






## Other visiulization
```{r}
tutor_group <- seda_mth %>%
  group_by(tutor_ID) %>%  # Group by tutor_ID
  select(tutor_ID,  # Keep tutor_ID in the selection
         student_group_talkmove_ratio_w, 
         Slope, 
         Intercept, 
         )  # Select the relevant columns



# Sample 10 random tutors
sampled_tutors <- tutor_group %>%
  ungroup() %>%  # Remove any grouping
  distinct(tutor_ID) %>%  # Get distinct tutor_IDs
  sample_n(20)  # Sample 10 random tutors

# Filter the original dataset to include only the sampled tutors
seda_mth_sampled <- seda_mth %>%
  filter(tutor_ID %in% sampled_tutors$tutor_ID)
```
 

```{r, fig.height=6, fig.width=13}
# Plot for the sampled students
seda_mth_sampled %>%
  ggplot(aes(x=student_group_talkmove_ratio_w, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +  # Scatter points
  geom_smooth(method="lm", se=FALSE, color="blue") +  # Linear regression line
  facet_wrap(~tutor_ID, nrow=3) +  # Facet by student
  ylab("Student Maths Slope") + 
  xlab("Student's Average Usage of Talkmoves") + 
  theme_bw(base_size=10) +  # Theme for better visualization
  theme(strip.text = element_text(size = 8))  # Adjust size of facet labels for clarity

ggsave(filename="statescatters_random10.png", height=6, width=13)
```

## Correlation of speaker level(unweighted  variable) aveargaing and session (weighted  variable) level averaging

```{r}
cor(seda_mth$unweighted_student_talkmove_ratio, seda_mth$weighted_student_talkmove_ratio)
cor(seda_mth$unweighted_tutor_talkmove_ratio, seda_mth$weighted_tutor_talkmove_ratio)
```


```{r}
cor(seda_mth$unweighted_student_utterance_ratio, seda_mth$weighted_student_utterance_ratio)
cor(seda_mth$unweighted_tutor_utterance_ratio, seda_mth$weighted_tutor_utterance_ratio)
```
## Corrlation of speaker's group talkmoves

```{r}
# Select relevant variables
data <- seda_mth[, c("student_group_talkmove_ratio_w", "tutor_talkmove_ratio_w")]  

#Calculate a correlation matrix
cor_matrix <- cor(data)

tab_corr(data)
```

## Corrlation of speaker's group utterance
```{r}
# Select relevant variables
data <- seda_mth[, c("student_group_utterance_ratio_w",	"tutor_utterance_ratio_w")]  


#Calculate a correlation matrix
cor_matrix <- cor(data)

tab_corr(data)
```



## Corrlation of Student Talkmove lables
```{r}
# Select relevant variables
data <- seda_mth[, c("student_group_relating_ratio_w",	"student_group_asking_for_info_ratio_w", "student_group_making_claim_ratio_w", "student_group_providing_evidence_ratio_w")]  


#Calculate a correlation matrix
cor_matrix <- cor(data)

tab_corr(data)
```

## Correlation of tutor's talkmove labels
```{r}
# Select relevant variables
data <- seda_mth[, c("tutor_keeping_together_w",	"tutor_students_relating_w", "tutor_restating_w", "tutor_revoicing_w", "tutor_reasoning_w")]

#Calculate a correlation matrix
cor_matrix <- cor(data)
tab_corr(data)
```



## MLM Modeling

### Speaker's Talkmove Ratios as Predictors
```{r}
#Adding Talkmove Predictors 01
model_01 <- lmer(Slope ~ student_group_talkmove_ratio_w + unique_session_IDs_count +
              (1 | student_tutor_group),
              data = seda_mth, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Talkmove Predictors 01
##model_011 <- rlmer(Slope ~ student_group_talkmove_ratio +
#              (1 | student_tutor_group),
#              data = seda_mth, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
#Adding Talkmove Predictors 03
model_03 <- lmer(Slope ~ tutor_talkmove_ratio_w + unique_session_IDs_count + 
              (1 | student_tutor_group),
              data = seda_mth, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
# Display the model summary
tab_model(model_01, model_03,  dv.labels = c("Student Group TalkMove",  "Tutor Talkmove"))
```



```{r}
#Adding Talkmove Predictors 04
model_04 <- blmer(Slope ~ student_group_talkmove_ratio_w + tutor_talkmove_ratio_w + unique_session_IDs_count + 
              (1 | student_tutor_group),
              data = seda_mth, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))
tab_model(model_04)

```


```{r}
#Adding Talkmove Predictors 04
#model_104 <- rlmer(Slope ~ student_group_talkmove_ratio + tutor_talkmove_ratio +
#              (1 | student_tutor_group),
#              data = seda_mth, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))
#tab_model(model_104)

```  
  
  
  
  
  
  
  


### Speaker's Utterance Ratios as Predictors

```{r}
#Adding Uterance Predictors 20
model_20 <- blmer(Slope ~ student_group_utterance_ratio_w + unique_session_IDs_count + 
              (1 | student_tutor_group),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```
  
  
```{r}
#Adding Uterance Predictors 23
model_23 <- blmer(Slope ~ tutor_utterance_ratio_w + unique_session_IDs_count + 
              (1 | student_tutor_group),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
# Display the model summary
tab_model(model_20, model_23,  dv.labels = c("Group Student Utterance",  "Tutor Utterance"))
```

```{r}
#Adding Uterance Predictors 24
model_24 <- blmer(Slope ~ student_group_utterance_ratio_w + tutor_utterance_ratio_w + unique_session_IDs_count +
              (1 | student_tutor_group),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
tab_model(model_24)
```








  
## Talkmove labels as Predictors
### Student Group Talkmove labels
```{r}
#Adding Individual Talkmove Predictors 30
model_30 <- blmer(Slope ~ student_group_relating_ratio_w + unique_session_IDs_count +
              (1  | student_tutor_group),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 31
model_31 <- blmer(Slope ~ student_group_asking_for_info_ratio_w + unique_session_IDs_count +
              (1 | student_tutor_group),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```
  

```{r}
#Adding Individual Talkmove Predictors 32
model_32 <- blmer(Slope ~ student_group_making_claim_ratio_w + unique_session_IDs_count +
              (1 | student_tutor_group),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_33 <- blmer(Slope ~ student_group_providing_evidence_ratio_w + unique_session_IDs_count +
              (1 | student_tutor_group),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```


```{r}
# Display the model summary
tab_model(model_30, model_31, model_32, model_33,  dv.labels = c("Student Relating", "Student Asking for Info", "Student making claim", "Student providing evidence"))
```








### USING THE ROBUST MODEL: Student Group Talkmove labels
<!-- # ```{r} -->
<!-- # #Adding Individual Talkmove Predictors 30 -->
<!-- # model_3067 <- rlmer(Slope ~ student_group_relating_ratio + -->
<!-- #               (1  | student_tutor_group), -->
<!-- #               data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa")) -->
<!-- # -->
<!-- # ``` -->
<!-- # -->
<!-- # ```{r} -->
<!-- # #Adding Individual Talkmove Predictors 31 -->
<!-- # model_3167 <- rlmer(Slope ~ student_group_asking_for_info_ratio + -->
<!-- #               (1 | student_tutor_group), -->
<!-- #               data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa")) -->
<!-- # -->
<!-- # ``` -->
<!-- # -->
<!-- # -->
<!-- # ```{r} -->
<!-- # #Adding Individual Talkmove Predictors 32 -->
<!-- # model_3267 <- rlmer(Slope ~ student_group_making_claim_ratio + -->
<!-- #               (1 | student_tutor_group), -->
<!-- #               data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa")) -->
<!-- # -->
<!-- # ``` -->
<!-- # -->
<!-- # ```{r} -->
<!-- # #Adding Individual Talkmove Predictors 32 -->
<!-- # model_3367 <- rlmer(Slope ~ student_group_providing_evidence_ratio + -->
<!-- #               (1 | student_tutor_group), -->
<!-- #               data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa")) -->
<!-- # -->
<!-- # ``` -->
<!-- # -->
<!-- # -->
<!-- # ```{r} -->
<!-- # # Display the model summary -->
<!-- # tab_model(model_3067, model_3167, model_3267, model_3367,  dv.labels = c("Student Relating", "Student Asking for Info", "Student making claim", "Student providing evidence")) -->
<!-- # ``` -->



### Tutor Talkmove labels
```{r}
#Adding Individual Talkmove Predictors 40
model_40 <- blmer(Slope ~ tutor_keeping_together_w + unique_session_IDs_count +
              (1 | student_tutor_group),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
#Adding Individual Talkmove Predictors 41
model_41 <- blmer(Slope ~ tutor_students_relating_w + unique_session_IDs_count +
              (1 | student_tutor_group),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
#Adding Individual Talkmove Predictors 42
model_42 <- blmer(Slope ~ tutor_restating_w + unique_session_IDs_count +
              (1 | student_tutor_group),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
#Adding Individual Talkmove Predictors 43
model_43 <- blmer(Slope ~ tutor_revoicing_w + unique_session_IDs_count +
              (1 | student_tutor_group),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
#Adding Individual Talkmove Predictors 44
model_44 <- blmer(Slope ~ tutor_reasoning_w + unique_session_IDs_count +
              (1 | student_tutor_group),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
# Display the model summary
tab_model(model_40, model_41, model_42, model_43, model_44,  dv.labels = c("Tutor Keeping Together", "Tutor Students Relating", "Tutor Restating", "Tutor Revoicing", "Tutor Reasoning"))
```





<!-- ### USING ROBUST MODEL: Tutor Talkmove labels -->
<!-- ```{r} -->
<!-- #Adding Individual Talkmove Predictors 40 -->
<!-- model_400 <- rlmer(Slope ~ tutor_keeping_together + -->
<!--               (1 | student_tutor_group), -->
<!--               data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa")) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #Adding Individual Talkmove Predictors 41 -->
<!-- model_410 <- rlmer(Slope ~ tutor_students_relating + -->
<!--               (1 | student_tutor_group), -->
<!--               data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa")) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #Adding Individual Talkmove Predictors 42 -->
<!-- model_420 <- rlmer(Slope ~ tutor_restating + -->
<!--               (1 | student_tutor_group), -->
<!--               data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa")) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #Adding Individual Talkmove Predictors 43 -->
<!-- model_430 <- rlmer(Slope ~ tutor_revoicing + -->
<!--               (1 | student_tutor_group), -->
<!--               data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa")) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #Adding Individual Talkmove Predictors 44 -->
<!-- model_440 <- rlmer(Slope ~ tutor_reasoning + -->
<!--               (1 | student_tutor_group), -->
<!--               data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa")) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # Display the model summary -->
<!-- tab_model(model_400, model_410, model_420, model_430, model_440,  dv.labels = c("Tutor Keeping Together", "Tutor Students Relating", "Tutor Restating", "Tutor Revoicing", "Tutor Reasoning")) -->
<!-- ``` -->





# Interaction Effects from Sidney
```{r}
data <- seda_mth;
data$student_talkmove_ratioWZ <- scale(DescTools::Winsorize(data$unweighted_student_talkmove_ratio,                                                   quantile(data$unweighted_student_talkmove_ratio, probs = c(0, 0.99), na.rm = TRUE)))
data$tutor_talkmove_ratioWZ <- scale(DescTools::Winsorize(data$unweighted_tutor_talkmove_ratio,  quantile(data$unweighted_tutor_talkmove_ratio, probs = c(0, .99), na.rm = T)))
data$tutor_utterance_ratioWZ <- scale(DescTools::Winsorize(data$unweighted_tutor_utterance_ratio,  quantile(data$unweighted_tutor_utterance_ratio, probs = c(0, .99), na.rm = T)))
data$tutor_talkmove_ratioZ <- scale(data$unweighted_tutor_talkmove_ratio)
data$unique_session_IDs_countoZ <- scale(data$unique_session_IDs_count)

hist(data$student_talkmove_ratioWZ)
hist(data$tutor_talkmove_ratioWZ)
hist(data$tutor_utterance_ratioWZ)
hist(data$tutor_talkmove_ratioZ)
hist(data$unique_session_IDs_countoZ)

m <- lmer(Slope ~ student_talkmove_ratioWZ *tutor_talkmove_ratioWZ + tutor_utterance_ratioWZ + unique_session_IDs_countoZ + (1| student_tutor_group), data = data, control = lmerControl(optimizer = "bobyqa"))

Anova(m, type = 3)
tab_model(m)

visreg::visreg(m, "student_talkmove_ratioWZ", by = "tutor_talkmove_ratioWZ", gg = T, breaks = c(-1, 0, 1))

Mod_list <- list(tutor_talkmove_ratioWZ = c(-1, 0, 1))

emtrends(m, ~student_talkmove_ratioWZ*tutor_talkmove_ratioWZ, var="student_talkmove_ratioWZ",at=Mod_list)

```
