---
title: "Student Engagmement"
author: "Kelechi Ezema"
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: true
knit: (function(inputFile, encoding) { 
          rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file= "Student_Tutor_new_augmented_model_emnlp.html") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r message=FALSE, warning=FALSE}
# load packages #####
library(tidyverse)  # data processing
library(haven)      # read in stata data
library(vtable)     # summary tables
library(labelled)   # to see and create variable labels
library(lme4)      # estimate MLM
library(sjPlot)    # regression tables
library(lmerTest)  # hypothesis testing for MLM
library(quantreg)
library(blme)
library(writexl)
library(openxlsx)
library(robustlmm)
library(DescTools)
library(reshape2)
library(robustlmm)
library(visreg)
library(emmeans)
library(car)

```


## Load Data

```{r}
# # Load the datasets
# student_tutor_file_asr_conf <- read.csv("student_tutor_ready_for_rcode_may_14th_asr_fine_augmented_with_confidence_filter_all_achievement.csv")
# student_tutor_file_asr_aug <- read.csv("student_tutor_ready_for_rcode_may_14th_asr_fine_augmented_all_achievement.csv")
# student_tutor_file_asr_fin <- read.csv("student_tutor_ready_for_rcode_may_14th_fine_tuned_all_achievement.csv")
# 
# # Define a function to select relevant columns
# select_relevant_columns <- function(data, columns) {
#   data %>% select(all_of(columns))
# }
# 
# # Specify the columns to keep for each dataset
# common_columns <- c(
#   "student_tutor_id", "unique_session_IDs_count", "I", "S",
#   "talkmove_proportion_mean", "utterance_proportion_mean", "words_proportion_mean",
#   "co_student_talkmove_proportion_mean_mean", "co_student_utterance_proportion_mean_mean",
#   "co_student_words_proportion_mean_mean", "tutor_talkmove_proportion_mean",
#   "tutor_utterance_proportion_mean", "tutor_words_proportion_mean", "student_relating_proportion_mean", "student_asking_for_info_proportion_mean", "student_making_claim_proportion_mean", "student_providing_evidence_proportion_mean", "co_student_relating_proportion_mean_mean", "co_student_asking_for_info_proportion_mean_mean", "co_student_making_claim_proportion_mean_mean", "co_student_providing_evidence_proportion_mean_mean", "tutor_keeping_together_proportion_mean", "tutor_students_relating_proportion_mean", "tutor_restating_proportion_mean", "tutor_revoicing_proportion_mean", "tutor_reasoning_proportion_mean", "tutor_accuracy_proportion_mean"
# )
# 
# augmented_columns <- c(
#   common_columns, "tutor_ID", "Anon.Student.ID", "Fellow.ID",
#   "baseline_how_much_like_math", "baseline_confidence_in_math_skills_abilities",
#   "baseline_comfortable_participating_in_math_class", "baseline_enjoy_mathematical_challenges",
#   "baseline_math_relationship_average_rating", "mid_year_how_much_like_math",
#   "mid_year_confidence_in_math_skills_abilities", "mid_year_comfortable_participating_in_math_class",
#   "mid_year_enjoy_mathematical_challenges", "mid_year_math_relationship_average_rating",
#   "mid_year_relationship_with_tutor", "final_how_much_like_math",
#   "final_confidence_in_math_skills_abilities", "final_comfortable_participating_in_math_class",
#   "final_enjoy_mathematical_challenges", "final_math_relationship_average_rating",
#   "final_relationship_with_tutor", "is_duplicated_survey",
#   "sumScore_1", "sumScore_2", "sumScore_3", "sumScore_4", "sumScore_5"
# )
# 
# # Select relevant columns for each dataset
# student_tutor_file_asr_conf <- select_relevant_columns(student_tutor_file_asr_conf, common_columns)
# student_tutor_file_asr_aug <- select_relevant_columns(student_tutor_file_asr_aug, augmented_columns)
# student_tutor_file_asr_fin <- select_relevant_columns(student_tutor_file_asr_fin, common_columns)
# 
# # Merge the datasets with suffixes
# merged_data <- student_tutor_file_asr_conf %>%
#   full_join(student_tutor_file_asr_aug, by = "student_tutor_id", suffix = c("_conf", "_aug")) %>%
#   full_join(student_tutor_file_asr_fin, by = "student_tutor_id", suffix = c("", "_fin"))
# 
# # Save the merged data as a CSV file
# write.csv(merged_data, "student_tutor_ready_for_rcode_may_16th_all_merged.csv", row.names = FALSE)


# Load merged data
merged_data <- read.csv("student_tutor_ready_for_rcode_may_16th_all_merged.csv")
```


## Self reported engagement
```{r}
data <- merged_data

data$mid_year_math_relationship_average_rating_conf <- as.numeric(data$mid_year_math_relationship_average_rating)

data$student_id <- data$Anon.Student.ID;
data$tutor_id <- data$Fellow.ID;

begin_vars <- colnames(merged_data)$c("baseline_how_much_like_math", "baseline_confidence_in_math_skills_abilities",  "baseline_comfortable_participating_in_math_class", "baseline_enjoy_mathematical_challenges",    "baseline_math_relationship_average_rating")

mid_vars <- colnames(merged_data)$c("mid_year_how_much_like_math", "mid_year_confidence_in_math_skills_abilities", "mid_year_comfortable_participating_in_math_class", "mid_year_enjoy_mathematical_challenges", "mid_year_math_relationship_average_rating_conf", "mid_year_relationship_with_tutor")

end_vars <- colnames(merged_data)$c("final_how_much_like_math", "final_confidence_in_math_skills_abilities", "final_comfortable_participating_in_math_class", "final_enjoy_mathematical_challenges", "final_math_relationship_average_rating", "final_relationship_with_tutor")


psych::alpha(data[begin_vars], na.rm = T)
psych::alpha(data[mid_vars], na.rm = T)
psych::alpha(data[end_vars], na.rm = T)

data$begin <- rowMeans(data[begin_vars], na.rm = T)
data$mid <- rowMeans(data[mid_vars], na.rm = T)
data$end <- rowMeans(data[end_vars], na.rm = T)


vars <- c("begin", "mid", "end");
psych::alpha(data[vars], na.rm = T)

data$engagement <- rowMeans(data[vars], na.rm = T)

tableone::CreateContTable(vars = vars, data = data);

data.melt <- melt(data[c(vars, "student_id", "tutor_id")], id = c("student_id", "tutor_id"))

m <- lmer(value ~ variable + (1 | student_id:tutor_id) + (1|tutor_id), data = data.melt)
tab_model(m)

emmeans::emmeans(m, pairwise ~ variable)

```




## Data Filterering

```{r}
student_tutor_data <- data

# # Calculate the average number of sessions per student_tutor_id
# student_tutor_data <- student_tutor_data %>%
#   group_by(student_id) %>%
#   mutate(unique_session_IDs_count = n_distinct(unique_session_IDs_count)) %>%
#   ungroup()
# 



# Select Student_Tutor_Group with unique_session_IDs_count > 10
student_tutor_data <- student_tutor_data %>% filter(unique_session_IDs_count >= 10)

#Select Student_Tutor_Group with achievement score
student_tutor_data <- student_tutor_data %>% filter(is.na(I) == FALSE)


dim(student_tutor_data)
```

## Column Renaming

```{r}
student_tutor_data <- student_tutor_data %>%
  mutate(
    #Model trained on Human and ASR Augmented transcript data
         student_tm_mean_aug = talkmove_proportion_mean_aug,
         student_utterance_mean_aug = utterance_proportion_mean_aug,
         student_word_mean_aug = words_proportion_mean_aug,
         co_student_tm_mean_aug = co_student_talkmove_proportion_mean_mean_aug,
         co_student_utterance_mean_aug = co_student_utterance_proportion_mean_mean_aug,
         co_student_word_mean_aug = co_student_words_proportion_mean_mean_aug,
         tutor_tm_mean_aug = tutor_talkmove_proportion_mean_aug,
         tutor_utterance_mean_aug = tutor_utterance_proportion_mean_aug,
         tutor_word_mean_aug = tutor_words_proportion_mean_aug,
         
         # Individual TM labels
         student_relating_mean_aug = student_relating_proportion_mean_aug,
         student_asking_info_mean_aug = student_asking_for_info_proportion_mean_aug,
         student_making_claim_mean_aug = student_making_claim_proportion_mean_aug,
         student_providing_evidence_mean_aug = student_providing_evidence_proportion_mean_aug,
         tutor_keeping_together_mean_aug = tutor_keeping_together_proportion_mean_aug,
         tutor_relating_mean_aug = tutor_students_relating_proportion_mean_aug,
         tutor_restating_mean_aug = tutor_restating_proportion_mean_aug,
         tutor_revoicing_mean_aug = tutor_revoicing_proportion_mean_aug,
         tutor_reasoning_mean_aug = tutor_reasoning_proportion_mean_aug,
         tutor_accuracy_mean_aug = tutor_accuracy_proportion_mean_aug,
         
    #Model trained on Human transcript data
         student_tm_mean_fin = talkmove_proportion_mean,
         student_utterance_mean_fin = utterance_proportion_mean,
         student_word_mean_fin = words_proportion_mean,
         co_student_tm_mean_fin = co_student_talkmove_proportion_mean_mean,
         co_student_utterance_mean_fin = co_student_utterance_proportion_mean_mean,
         co_student_word_mean_fin = co_student_words_proportion_mean_mean,
         tutor_tm_mean_fin = tutor_talkmove_proportion_mean,
         tutor_utterance_mean_fin = tutor_utterance_proportion_mean,
         tutor_word_mean_fin = tutor_words_proportion_mean,
    
         # Individual TM labels
         student_relating_mean_fin = student_relating_proportion_mean,
         student_asking_info_mean_fin = student_asking_for_info_proportion_mean,
         student_making_claim_mean_fin = student_making_claim_proportion_mean,
         student_providing_evidence_mean_fin = student_providing_evidence_proportion_mean,
         tutor_keeping_together_mean_fin = tutor_keeping_together_proportion_mean,
         tutor_relating_mean_fin = tutor_students_relating_proportion_mean,
         tutor_restating_mean_fin = tutor_restating_proportion_mean,
         tutor_revoicing_mean_fin = tutor_revoicing_proportion_mean,
         tutor_reasoning_mean_fin = tutor_reasoning_proportion_mean,
         tutor_accuracy_mean_fin = tutor_accuracy_proportion_mean,
    
         
    #Model trained on Human and ASR Augmented transcript data with confidence filtering     
         student_tm_mean_conf = talkmove_proportion_mean_conf,
         student_utterance_mean_conf = utterance_proportion_mean_conf,
         student_word_mean_conf = words_proportion_mean_conf,
         co_student_tm_mean_conf = co_student_talkmove_proportion_mean_mean_conf,
         co_student_utterance_mean_conf = co_student_utterance_proportion_mean_mean_conf,
         co_student_word_mean_conf = co_student_words_proportion_mean_mean_conf,
         tutor_tm_mean_conf = tutor_talkmove_proportion_mean_conf,
         tutor_utterance_mean_conf = tutor_utterance_proportion_mean_conf,
         tutor_word_mean_conf = tutor_words_proportion_mean_conf,
    
         # Individual TM labels
         student_relating_mean_conf = student_relating_proportion_mean_conf,
         student_asking_info_mean_conf = student_asking_for_info_proportion_mean_conf,
         student_making_claim_mean_conf = student_making_claim_proportion_mean_conf,
         student_providing_evidence_mean_conf = student_providing_evidence_proportion_mean_conf,
         tutor_keeping_together_mean_conf = tutor_keeping_together_proportion_mean_conf,
         tutor_relating_mean_conf = tutor_students_relating_proportion_mean_conf,
         tutor_restating_mean_conf = tutor_restating_proportion_mean_conf,
         tutor_revoicing_mean_conf = tutor_revoicing_proportion_mean_conf,
         tutor_reasoning_mean_conf = tutor_reasoning_proportion_mean_conf,
         tutor_accuracy_mean_conf = tutor_accuracy_proportion_mean_conf,
         
         
         Intercept = I,
         Slope = S,
         num_sessions_fin = unique_session_IDs_count,
  )

```







## Rescaling Achievement Intercept and Slope

```{r}
student_tutor_data <- student_tutor_data %>%
  mutate(
         Slope = Slope *100,
         Intercept = Intercept*100
  )

```



## Histogram for predictors before winsorization
```{r}
plot_histogram <- function(df, vars, id)
{
  data.plot <- melt(df[c(id, vars)],  id = id);
  ggplot(data.plot, aes(x = value)) + geom_histogram() + facet_wrap(~variable, scales = "free")
}


# Define the base variables
vars <- c("student_tm_mean", "student_utterance_mean", "student_word_mean", 
          "co_student_tm_mean", "co_student_utterance_mean", "co_student_word_mean",
          "tutor_tm_mean", "tutor_utterance_mean", "tutor_word_mean", 
          "student_relating_mean", "student_asking_info_mean", "student_making_claim_mean", "student_providing_evidence_mean", "tutor_keeping_together_mean", "tutor_relating_mean", "tutor_restating_mean", "tutor_revoicing_mean",
          "tutor_reasoning_mean", "tutor_accuracy_mean")

# Generate variables for each suffix
vars_aug <- paste0(vars, "_aug")
vars_fin <- paste0(vars, "_fin")
vars_conf <- paste0(vars, "_conf")

# Plot histograms for _conf, _fin, and _aug cases
plot_histogram(student_tutor_data, vars_aug, id = "student_tutor_id")
# plot_histogram(student_tutor_data, vars_fin, id = "student_tutor_id")
# plot_histogram(student_tutor_data, vars_conf, id = "student_tutor_id")


```


## Winzeration and normalization of Predictor variables
```{r}
#Winsorize the variables

# Loop through each variable in vars_aug, vars_fin, vars_conf
for (var_list in list(vars_aug, vars_fin, vars_conf)) {
  for (var in var_list) {
    # Apply Winsorization and scaling
    student_tutor_data[paste0(var, "_ZW")] <- scale(
      DescTools::Winsorize(
        student_tutor_data[[var]], 
        quantile(student_tutor_data[[var]], probs = c(0.0, 0.99), na.rm = TRUE)
      )
    )
  }
}

# winsorize the num_sessions
student_tutor_data$num_sessions_ZW <- scale(
  DescTools::Winsorize(
    student_tutor_data$num_sessions_fin, 
    quantile(student_tutor_data$num_sessions_fin, probs = c(0.0, 0.99), na.rm = TRUE)
  )
)
```




<!-- ## Cummulate Frequency Table of data   -->
<!-- ```{r} -->

<!-- freq_table <- function(x) -->
<!-- { -->
<!--   return(cbind(Freq=table(x), Cumul=cumsum(prop.table(table(x))), relative=prop.table(table(x)))); -->
<!-- } -->

<!-- # Print the frequency table in 2 decimal places -->
<!-- freq_table(round(student_tutor_data$num_sessions_ZW, 1) ) -->


<!-- ``` -->


## Histogram for predictors after winsorization
```{r}
# Add the _ZW suffix to each variable list
vars_aug_ZW <- paste0(vars_aug, "_ZW")
vars_fin_ZW <- paste0(vars_fin, "_ZW")
vars_conf_ZW <- paste0(vars_conf, "_ZW")

# Plot histograms for each case
plot_histogram(student_tutor_data, vars_aug_ZW, id = "student_tutor_id")
# plot_histogram(student_tutor_data, vars_fin_ZW, id = "student_tutor_id")
# plot_histogram(student_tutor_data, vars_conf_ZW, id = "student_tutor_id")


```


## Corrlation of independent variables 

```{r}
# Show correlation matrix for only vars_aug_ZW
data_aug_total_TM <- student_tutor_data[, c("Intercept", "student_tm_mean_aug_ZW", "student_utterance_mean_aug_ZW", "student_word_mean_aug_ZW", "co_student_tm_mean_aug_ZW", "co_student_utterance_mean_aug_ZW", "co_student_word_mean_aug_ZW", "tutor_tm_mean_aug_ZW", "tutor_utterance_mean_aug_ZW", "tutor_word_mean_aug_ZW", "num_sessions_ZW")]

data_aug_student_TM <- student_tutor_data[, c("student_relating_mean_aug_ZW", "student_asking_info_mean_aug_ZW", "student_making_claim_mean_aug_ZW", "student_providing_evidence_mean_aug_ZW", "student_tm_mean_aug_ZW", "student_utterance_mean_aug_ZW", "student_word_mean_aug_ZW", "num_sessions_ZW")]

data_aug_tutor_TM <- student_tutor_data[, c("tutor_keeping_together_mean_aug_ZW", "tutor_relating_mean_aug_ZW", "tutor_restating_mean_aug_ZW", "tutor_revoicing_mean_aug_ZW", "tutor_reasoning_mean_aug_ZW", "tutor_accuracy_mean_aug_ZW", "tutor_tm_mean_aug_ZW", "tutor_utterance_mean_aug_ZW", "tutor_word_mean_aug_ZW", "num_sessions_ZW")]

# Calculate correlation matrices
cor_matrix_aug_total <- cor(data_aug_total_TM)
cor_matrix_aug_student <- cor(data_aug_student_TM)
cor_matrix_aug_tutor <- cor(data_aug_tutor_TM)




# tab_corr for a formatted correlation table
tab_corr(cor_matrix_aug_total)
tab_corr(cor_matrix_aug_student)
tab_corr(cor_matrix_aug_tutor)
```

## MLM Modeling

### Slope ~ student_tm_mean
```{r}
model_01 <- blmer(Slope ~ Intercept +  student_tm_mean_aug_ZW + co_student_tm_mean_aug_ZW + student_utterance_mean_aug_ZW + co_student_utterance_mean_aug_ZW + tutor_tm_mean_aug_ZW + num_sessions_ZW +
              (1 | tutor_ID),
              data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))


model_02 <- blmer(Slope ~ Intercept +  student_tm_mean_fin_ZW + co_student_tm_mean_fin_ZW + student_utterance_mean_fin_ZW + co_student_utterance_mean_fin_ZW + tutor_tm_mean_fin_ZW + num_sessions_ZW +
              (1 | tutor_ID),
              data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))


# model_03 <- blmer(Slope ~ Intercept + student_tm_mean_conf_ZW + co_student_tm_mean_conf_ZW + student_utterance_mean_conf_ZW + co_student_utterance_mean_conf_ZW + tutor_tm_mean_conf_ZW + num_sessions_ZW +
#               (1 | tutor_ID),
#               data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))


tab_model(model_01, model_02, show.std = T)

vif(model_01)
vif(model_02)
# vif(model_03)
```






### engagement ~ student_tm_mean
```{r}
model_01 <- blmer(engagement ~ Intercept + student_tm_mean_aug_ZW + co_student_tm_mean_aug_ZW + student_utterance_mean_aug_ZW + co_student_utterance_mean_aug_ZW + tutor_tm_mean_aug_ZW + num_sessions_ZW +
              (1 | tutor_ID),
              data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))

model_02 <- blmer(engagement ~ Intercept + student_tm_mean_fin_ZW + co_student_tm_mean_fin_ZW + student_utterance_mean_fin_ZW + co_student_utterance_mean_fin_ZW + tutor_tm_mean_fin_ZW + num_sessions_ZW +
              (1 | tutor_ID),
              data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))

# model_03 <- blmer(engagement ~ Intercept + student_tm_mean_conf_ZW + co_student_tm_mean_conf_ZW + student_utterance_mean_conf_ZW + co_student_utterance_mean_conf_ZW + tutor_tm_mean_conf_ZW + num_sessions_ZW +
#               (1 | tutor_ID),
#               data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))

tab_model(model_01, model_02, show.std = T)

vif(model_01)
vif(model_02)
# vif(model_03)
```



<!-- ### Slope ~ student_tm_mean Interaction with co_student_tm_mean -->
<!-- ```{r} -->
<!-- model_01 <- blmer(Slope ~ student_tm_mean_aug_ZW*co_student_tm_mean_aug_ZW + student_utterance_mean_aug_ZW + co_student_utterance_mean_aug_ZW + tutor_tm_mean_aug_ZW*student_tm_mean_aug_ZW + num_sessions_ZW + -->
<!--               (1 | tutor_ID), -->
<!--               data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa")) -->

<!-- model_02 <- blmer(Slope ~ student_tm_mean_fin_ZW*co_student_tm_mean_fin_ZW + student_utterance_mean_fin_ZW + co_student_utterance_mean_fin_ZW + tutor_tm_mean_fin_ZW*student_tm_mean_fin_ZW + num_sessions_ZW + -->
<!--               (1 | tutor_ID), -->
<!--               data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa")) -->

<!-- model_03 <- blmer(Slope ~ student_tm_mean_conf_ZW*co_student_tm_mean_conf_ZW + student_utterance_mean_conf_ZW + co_student_utterance_mean_conf_ZW + tutor_tm_mean_conf_ZW*student_tm_mean_conf_ZW + num_sessions_ZW + -->
<!--               (1 | tutor_ID), -->
<!--               data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa")) -->


<!-- tab_model(model_01, model_02, model_03) -->

<!-- vif(model_01) -->
<!-- vif(model_02) -->
<!-- vif(model_03) -->
<!-- ``` -->



### engagement ~ Individual TM labels
```{r}
model_01 <- blmer(engagement ~ Intercept + student_relating_mean_aug_ZW + student_asking_info_mean_aug_ZW + student_making_claim_mean_aug_ZW + student_providing_evidence_mean_aug_ZW + tutor_keeping_together_mean_aug_ZW + tutor_relating_mean_aug_ZW + tutor_restating_mean_aug_ZW + tutor_revoicing_mean_aug_ZW + tutor_reasoning_mean_aug_ZW + tutor_accuracy_mean_aug_ZW +  co_student_tm_mean_aug_ZW + student_utterance_mean_aug_ZW + co_student_utterance_mean_aug_ZW +  num_sessions_ZW +
              (1 | tutor_ID),
              data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))

model_02 <- blmer(engagement ~ Intercept + student_relating_mean_fin_ZW + student_asking_info_mean_fin_ZW + student_making_claim_mean_fin_ZW + student_providing_evidence_mean_fin_ZW + tutor_keeping_together_mean_fin_ZW + tutor_relating_mean_fin_ZW + tutor_restating_mean_fin_ZW + tutor_revoicing_mean_fin_ZW + tutor_reasoning_mean_fin_ZW + tutor_accuracy_mean_fin_ZW +  co_student_tm_mean_fin_ZW + student_utterance_mean_fin_ZW + co_student_utterance_mean_fin_ZW +  num_sessions_ZW +
              (1 | tutor_ID),
              data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))

# model_03 <- blmer(engagement ~ tutor_keeping_together_mean_fin_ZW + tutor_relating_mean_fin_ZW + tutor_restating_mean_fin_ZW + tutor_revoicing_mean_fin_ZW + tutor_reasoning_mean_fin_ZW + tutor_accuracy_mean_fin_ZW + tutor_utterance_mean_fin_ZW +  num_sessions_ZW +
#               (1 | tutor_ID),
#               data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))


 
tab_model(model_01, model_02, show.std = T)

vif(model_01)
vif(model_02)
# vif(model_03)
```


<!-- ### engagement ~ Individual Student TM labels -->
<!-- ```{r} -->
<!-- model_01 <- blmer(engagement ~ student_relating_mean_aug_ZW + student_asking_info_mean_aug_ZW + student_making_claim_mean_aug_ZW + student_providing_evidence_mean_aug_ZW + student_utterance_mean_aug_ZW +  num_sessions_ZW + -->
<!--               (1 | tutor_ID), -->
<!--               data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa")) -->


<!-- model_02 <- blmer(engagement ~ student_relating_mean_conf_ZW + student_asking_info_mean_conf_ZW + student_making_claim_mean_conf_ZW + student_providing_evidence_mean_conf_ZW + student_utterance_mean_conf_ZW +  num_sessions_ZW + -->
<!--               (1 | tutor_ID), -->
<!--               data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa")) -->


<!-- model_03 <- blmer(engagement ~ student_relating_mean_fin_ZW + student_asking_info_mean_fin_ZW + student_making_claim_mean_fin_ZW + student_providing_evidence_mean_fin_ZW + student_utterance_mean_fin_ZW +  num_sessions_ZW + -->
<!--               (1 | tutor_ID), -->
<!--               data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa")) -->



<!-- tab_model(model_01, model_02, model_03) -->

<!-- vif(model_01) -->
<!-- vif(model_02) -->
<!-- vif(model_03) -->
<!-- ``` -->