---
title: "Student Engagmement"
author: "Kelechi Ezema"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r}
# load packages #####
library(tidyverse)  # data processing
library(haven)      # read in stata data
library(vtable)     # summary tables
library(labelled)   # to see and create variable labels
library(lme4)      # estimate MLM
library(sjPlot)    # regression tables
library(lmerTest)  # hypothesis testing for MLM
library(quantreg)
library(blme)
library(writexl)
library(openxlsx)
library(robustlmm)
library(DescTools)
library(reshape2)
library(visreg)
library(emmeans)
library(car)

```


## Load Data

```{r}
#seda <- read.csv(file = "feb13_student_talkmove_achievement_merged.csv")
seda <- read.csv(file = "jan26_student_talkmove_achievement_merged")
```



## Data Filterering

```{r}
seda_mth <- seda

#Select Student in achievement file
seda_mth <- seda_mth %>% filter(is_in_achievement == 1)

#Select Student_Tutor with no multiple achievement score
seda_mth <- seda_mth %>% filter(is_duplicated_student_tutor_x == 0)

# Select Student_Tutor with unique_session_IDs_count > 10
seda_mth <- seda_mth %>% filter(unique_session_IDs_count >= 10)

# Select Student_Tutor with a tutor in the session
seda_mth <- seda_mth %>% filter(unique_tutor_id_received_talkmove_count == 1)

# Select Student_Tutor with a tutor in the session
#seda_mth <- seda_mth %>% filter(Processing_needed == 0)

dim(seda_mth)
```
## Column Renaming

```{r}
#Unweighted variables implies speaker level averaging
seda_mth <- seda_mth %>%
  mutate(
         student_talkmove_ratio = unweighted_student_talkmove_ratio,
         co_student_talkmove_ratio = unweighted_co_student_talkmove_ratio,
         student_utterance_ratio = unweighted_student_utterance_ratio,
         co_student_utterance_ratio = unweighted_co_student_utterance_ratio,
         tutor_talkmove_ratio = unweighted_tutor_talkmove_ratio,
         tutor_utterance_ratio = unweighted_tutor_utterance_ratio,
         student_relating_ratio = unweighted_student_relating_ratio,
         student_asking_for_info_ratio = unweighted_student_asking_for_info_ratio,
         student_making_claim_ratio = unweighted_student_making_claim_ratio,
         student_providing_evidence_ratio = unweighted_student_providing_evidence_ratio,
         Intercept = I,
         Slope = S,
         co_student_relating_ratio = unweighted_co_student_relating_ratio,
         co_student_asking_for_info_ratio = unweighted_co_student_asking_for_info_ratio,
         co_student_making_claim_ratio = unweighted_co_student_making_claim_ratio,
         co_student_providing_evidence_ratio = unweighted_co_student_providing_evidence_ratio,
         tutor_keeping_together = unweighted_tutor_keeping_together_ratio,
         tutor_students_relating = unweighted_tutor_students_relating_ratio,
         tutor_restating = unweighted_tutor_restating_ratio,
         tutor_revoicing = unweighted_tutor_revoicing_ratio,
         tutor_reasoning = unweighted_tutor_reasoning_ratio,
         
  )

```

## mahalanobis Distance (Not used in the analysis)
```{r eval=FALSE, include=FALSE}
seda_mth$student_talkmove_ratio_m <- mahalanobis(seda_mth[,c("student_talkmove_ratio", "co_student_talkmove_ratio", "tutor_talkmove_ratio", "student_utterance_ratio", "co_student_utterance_ratio", "tutor_utterance_ratio", "student_relating_ratio", "student_asking_for_info_ratio", "student_making_claim_ratio", "student_providing_evidence_ratio", "co_student_relating_ratio", "co_student_asking_for_info_ratio", "co_student_making_claim_ratio", "co_student_providing_evidence_ratio", "tutor_keeping_together", "tutor_students_relating", "tutor_restating", "tutor_revoicing", "tutor_reasoning")],
                                                 center = colMeans(seda_mth[,c("student_talkmove_ratio", "co_student_talkmove_ratio", "tutor_talkmove_ratio", "student_utterance_ratio", "co_student_utterance_ratio", "tutor_utterance_ratio", "student_relating_ratio", "student_asking_for_info_ratio", "student_making_claim_ratio", "student_providing_evidence_ratio", "co_student_relating_ratio", "co_student_asking_for_info_ratio", "co_student_making_claim_ratio", "co_student_providing_evidence_ratio", "tutor_keeping_together", "tutor_students_relating", "tutor_restating", "tutor_revoicing", "tutor_reasoning")]),
                                                 cov = cov(seda_mth[,c("student_talkmove_ratio", "co_student_talkmove_ratio", "tutor_talkmove_ratio")]),
                                                 inverted = FALSE)

```





## Winzeration of Predictor variables
```{r}
#Winsorize the variables

Vars <- c("student_talkmove_ratio", "co_student_talkmove_ratio", "tutor_talkmove_ratio", "student_utterance_ratio", "co_student_utterance_ratio", "tutor_utterance_ratio", "student_relating_ratio", "student_asking_for_info_ratio", "student_making_claim_ratio", "student_providing_evidence_ratio", "co_student_relating_ratio", "co_student_asking_for_info_ratio", "co_student_making_claim_ratio", "co_student_providing_evidence_ratio", "tutor_keeping_together", "tutor_students_relating", "tutor_restating", "tutor_revoicing", "tutor_reasoning")

for (var in Vars) {
  seda_mth[paste0(var, "_w")] <- scale(Winsorize(seda_mth[[var]], quantile(seda_mth[[var]], probs=c(0, 0.99), na.rm = FALSE)))
}

# Plot histogram of the winsorized variables
hist(seda_mth$student_talkmove_ratio_w)
hist(seda_mth$co_student_talkmove_ratio_w)
hist(seda_mth$tutor_talkmove_ratio_w)
hist(seda_mth$student_utterance_ratio_w)
hist(seda_mth$co_student_utterance_ratio_w)
hist(seda_mth$tutor_utterance_ratio_w)
hist(seda_mth$student_relating_ratio_w)
hist(seda_mth$student_asking_for_info_ratio_w)
hist(seda_mth$student_making_claim_ratio_w)
hist(seda_mth$student_providing_evidence_ratio_w)
hist(seda_mth$co_student_relating_ratio_w)
hist(seda_mth$co_student_asking_for_info_ratio_w)
hist(seda_mth$co_student_making_claim_ratio_w)
hist(seda_mth$co_student_providing_evidence_ratio_w)
hist(seda_mth$tutor_keeping_together_w)
hist(seda_mth$tutor_students_relating_w)
hist(seda_mth$tutor_restating_w)
hist(seda_mth$tutor_revoicing_w)
hist(seda_mth$tutor_reasoning_w)

```





## Rescaling Achievement Intercept and Slope

```{r}
seda_mth <- seda_mth %>%
  mutate(
         Slope = Slope *100,
         Intercept = Intercept*100
  )

```


## Level 1 Descriptives

```{r}
# Get the summary and store it in a variable
lev1 <- seda_mth %>%
  select(student_talkmove_ratio_w,student_utterance_ratio_w, co_student_talkmove_ratio_w,  co_student_utterance_ratio_w, Slope, Intercept, unique_session_IDs_count)
  sumtable(lev1)
```


## Level 2 Descriptives

```{r}
lev2 <- seda_mth %>%
  group_by(tutor_ID) %>%
  summarise(
    Assigned_unique_student=n(),
    Mean_tutor_talkmove=mean(tutor_talkmove_ratio_w),
    Mean_tutor_utterance=mean(tutor_utterance_ratio_w)
  ) %>%
  ungroup() %>%
  select(-tutor_ID)
sumtable(lev2, digits=2)
```



## Histograms

```{r}
ggplot(aes(x=Slope), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Student's Slope of maths scores") +
  ylab("Count") +
  theme_bw() 
```



```{r}
ggplot(aes(x=Intercept), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Student's Intercept of maths scores") +
  ylab("Count") +
  theme_bw() 
```




## Talkmove Histogram for speaker type

```{r}
ggplot(aes(x=student_talkmove_ratio_w), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Student's Proportion of Talkmove") +
  ylab("Count") +
  theme_bw() 
```

```{r}
ggplot(aes(x=co_student_talkmove_ratio_w), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Co-student's Proportion of Talkmove") +
  ylab("Count") +
  theme_bw() 
```


```{r}
ggplot(aes(x=tutor_talkmove_ratio_w), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Tutor's Proportion of Talkmove") +
  ylab("Count") +
  theme_bw() 
```

## Utterance Histogram for speaker type
```{r}
ggplot(aes(x=student_utterance_ratio_w), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Student's Utterance Proportion") +
  ylab("Count") +
  theme_bw() 
```
```{r}
ggplot(aes(x=co_student_utterance_ratio_w), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Co-student's Utterance Proportion") +
  ylab("Count") +
  theme_bw() 
```

```{r}
ggplot(aes(x=tutor_utterance_ratio_w), data = seda_mth) +
  geom_histogram(fill="grey",color="black") +
  xlab("Histogram of Tutor's Utterance Proportion") +
  ylab("Count") +
  theme_bw() 
```



## Speaker's Talkmove Scattarplot

```{r}
seda_mth %>%
  ggplot(aes(x=student_talkmove_ratio_w, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Maths score Slope") +
  xlab("Student's talkmoves proportion") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)
```



```{r}
seda_mth %>%
  ggplot(aes(x=co_student_talkmove_ratio_w, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Maths score Slope") +
  xlab("Co Student's talkmoves proportion") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)
```



```{r}
seda_mth %>%
  ggplot(aes(x=tutor_talkmove_ratio_w, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Maths score Slope") +
  xlab("Tutor's talkmoves proportion") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)
```


## Speaker's Utterance Scatterplots

```{r}
seda_mth %>%
  ggplot(aes(x=student_utterance_ratio_w, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Maths score Slope") +
  xlab("Student's utterance proportion") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)
```



```{r}
seda_mth %>%
  ggplot(aes(x=co_student_utterance_ratio_w, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Maths score Slope") +
  xlab("Co Student's utterance proportion") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)
```

```{r}
seda_mth %>%
  ggplot(aes(x=tutor_utterance_ratio_w, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +
  geom_smooth() +
  ylab("Student Maths score Slope") +
  xlab("Tutor utterance proportion") +
  theme_bw()
ggsave(filename="pooledscatter.png", height=4, width=6.5)
```






## Other visiulization
```{r}
tutor_group <- seda_mth %>%
  group_by(tutor_ID) %>%  # Group by tutor_ID
  select(tutor_ID,  # Keep tutor_ID in the selection
         student_talkmove_ratio_w, 
         Slope, 
         Intercept, 
         )  # Select the relevant columns



# Sample 10 random tutors
sampled_tutors <- tutor_group %>%
  ungroup() %>%  # Remove any grouping
  distinct(tutor_ID) %>%  # Get distinct tutor_IDs
  sample_n(20)  # Sample 10 random tutors

# Filter the original dataset to include only the sampled tutors
seda_mth_sampled <- seda_mth %>%
  filter(tutor_ID %in% sampled_tutors$tutor_ID)
```
 

```{r, fig.height=6, fig.width=13}
# Plot for the sampled students
seda_mth_sampled %>%
  ggplot(aes(x=student_talkmove_ratio_w, y=Slope)) +
  geom_point(pch=21, alpha=0.75, fill="grey") +  # Scatter points
  geom_smooth(method="lm", se=FALSE, color="blue") +  # Linear regression line
  facet_wrap(~tutor_ID, nrow=3) +  # Facet by student
  ylab("Student Maths Slope") + 
  xlab("Student's Average Usage of Talkmoves") + 
  theme_bw(base_size=10) +  # Theme for better visualization
  theme(strip.text = element_text(size = 8))  # Adjust size of facet labels for clarity

ggsave(filename="statescatters_random10.png", height=6, width=13)
```

## Correlation of speaker level(unweighted  variable) aveargaing and session (weighted  variable) level averaging

```{r}
cor(seda_mth$unweighted_student_talkmove_ratio, seda_mth$weighted_student_talkmove_ratio)
cor(seda_mth$unweighted_co_student_talkmove_ratio, seda_mth$weighted_co_student_talkmove_ratio)
cor(seda_mth$unweighted_tutor_talkmove_ratio, seda_mth$weighted_tutor_talkmove_ratio)
```


```{r}
cor(seda_mth$unweighted_student_utterance_ratio, seda_mth$weighted_student_utterance_ratio)
cor(seda_mth$unweighted_co_student_utterance_ratio, seda_mth$weighted_co_student_utterance_ratio)
cor(seda_mth$unweighted_tutor_utterance_ratio, seda_mth$weighted_tutor_utterance_ratio)
```



## Corrlation of speaker's talkmoves
```{r}
# Select relevant variables
data <- seda_mth[, c("student_talkmove_ratio_w",	"co_student_talkmove_ratio_w", "tutor_talkmove_ratio_w")]  

#Calculate a correlation matrix
cor_matrix <- cor(data)

tab_corr(data)
```

## Corrlation of speaker's utterance rate
```{r}
# Select relevant variables
data <- seda_mth[, c("student_utterance_ratio_w",	"co_student_utterance_ratio_w", "tutor_utterance_ratio_w")]  


#Calculate a correlation matrix
cor_matrix <- cor(data)

tab_corr(data)
```

## Correlation of student's talkmove labels
```{r}
# Select relevant variables
data <- seda_mth[, c("student_relating_ratio_w",	"student_asking_for_info_ratio_w", "student_making_claim_ratio_w", "student_providing_evidence_ratio_w")]

#Calculate a correlation matrix
cor_matrix <- cor(data)
tab_corr(data)
```

## Correlation of co-student's talkmove labels
```{r}
# Select relevant variables
data <- seda_mth[, c("co_student_relating_ratio_w",	"co_student_asking_for_info_ratio_w", "co_student_making_claim_ratio_w", "co_student_providing_evidence_ratio_w")]

#Calculate a correlation matrix
cor_matrix <- cor(data)
tab_corr(data)
```

## Correlation of tutor's talkmove labels
```{r}
# Select relevant variables
data <- seda_mth[, c("tutor_keeping_together_w",	"tutor_students_relating_w", "tutor_restating_w", "tutor_revoicing_w", "tutor_reasoning_w")]

#Calculate a correlation matrix
cor_matrix <- cor(data)
tab_corr(data)
```




## MLM Modeling

### Speaker's Talkmove Ratios as Predictors
```{r}
#Adding Talkmove Predictors 01
model_01 <- blmer(Slope ~ student_talkmove_ratio_w +
              (1 + student_talkmove_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
#tab_model(model_01)

```
  

```{r}
#Adding Talkmove Predictors 02
model_02 <- blmer(Slope ~ co_student_talkmove_ratio_w +
              (1 + co_student_talkmove_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```
  
  
```{r}
#Adding Talkmove Predictors 03
model_03 <- blmer(Slope ~ tutor_talkmove_ratio_w +
              (1 | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
# Display the model summary
tab_model(model_01, model_02, model_03,  dv.labels = c("Student TalkMove", "Co student Talkmove", "Tutor Talkmove"))
```
  

### Combined speaker talkmove ratios as predictors
```{r}
model_040 <- blmer(Slope ~ student_talkmove_ratio_w + co_student_talkmove_ratio_w + tutor_talkmove_ratio_w +
              (1 + student_talkmove_ratio_w + co_student_talkmove_ratio_w  | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
tab_model(model_040)
```



### Combined speaker talkmove ratios as predictors
```{r}
model_0402 <- rlmer(Slope ~ student_talkmove_ratio + co_student_talkmove_ratio + tutor_talkmove_ratio +
              (1 + student_talkmove_ratio + co_student_talkmove_ratio  | tutor_ID),
              data = seda_mth, REML = FALSE)
tab_model(model_0402)
```

  
  
  



### USING ROBUST MODEL: Speaker's Talkmove Ratios as Predictors
```{r}
#Adding Talkmove Predictors 01
model_901 <- rlmer(Slope ~ student_talkmove_ratio +
              (1 + student_talkmove_ratio | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
#tab_model(model_01)

```
  

```{r}
#Adding Talkmove Predictors 02
model_902 <- rlmer(Slope ~ co_student_talkmove_ratio +
              (1 + co_student_talkmove_ratio | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```
  
  
```{r}
#Adding Talkmove Predictors 03
model_903 <- rlmer(Slope ~ tutor_talkmove_ratio +
              (1 | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
# Display the model summary
tab_model(model_901, model_902, model_903,  dv.labels = c("Student TalkMove", "Co student Talkmove", "Tutor Talkmove"))
```
  


### Speaker's Uterance Ratios as Predictors

```{r}
#Adding Uterance Predictors 20
model_20 <- blmer(Slope ~ student_utterance_ratio_w +
              (1 + student_utterance_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```
  

```{r}
#Adding Uterance Predictors 22
model_22 <- blmer(Slope ~ co_student_utterance_ratio_w +
              (1 + co_student_utterance_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```
  
  
```{r}
#Adding Uterance Predictors 23
model_23 <- blmer(Slope ~ tutor_utterance_ratio_w +
              (1 | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
```

```{r}
# Display the model summary
tab_model(model_20, model_22, model_23,  dv.labels = c("Student Utterance", "Co student Utterance", "Tutor Utterance"))
```



## Talkmove Labels by Speaker Type as Predictors

### Talkmove by Student
```{r}
#Adding Individual Talkmove Predictors 30
model_301 <- blmer(Slope ~ student_relating_ratio_w +
              (1 + student_relating_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 31
model_311 <- blmer(Slope ~ student_asking_for_info_ratio_w +
              (1 + student_asking_for_info_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```
  

```{r}
#Adding Individual Talkmove Predictors 32
model_321 <- blmer(Slope ~ student_making_claim_ratio_w +
              (1 + student_making_claim_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_331 <- blmer(Slope ~ student_providing_evidence_ratio_w +
              (1 + student_providing_evidence_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```


```{r}
# Display the model summary
tab_model(model_301, model_311, model_321, model_331,  dv.labels = c("Student Relating", "Student Asking for Info", "Student making claim", "Student providing evidence"))
```









### USING ROBUST MODEL: Talkmove by Student
```{r}
#Adding Individual Talkmove Predictors 30
model_9301 <- rlmer(Slope ~ student_relating_ratio +
              (1 + student_relating_ratio | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 31
model_9311 <- rlmer(Slope ~ student_asking_for_info_ratio +
              (1 + student_asking_for_info_ratio | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```
  

```{r}
#Adding Individual Talkmove Predictors 32
model_9321 <- rlmer(Slope ~ student_making_claim_ratio +
              (1 + student_making_claim_ratio | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_9331 <- rlmer(Slope ~ student_providing_evidence_ratio +
              (1 + student_providing_evidence_ratio | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```


```{r}
# Display the model summary
tab_model(model_9301, model_9311, model_9321, model_9331,  dv.labels = c("Student Relating", "Student Asking for Info", "Student making claim", "Student providing evidence"))
```




### Talkmove by Co Student
```{r}
#Adding Individual Talkmove Predictors 30
model_30 <- blmer(Slope ~ co_student_relating_ratio_w +
              (1 + co_student_relating_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 31
model_31 <- blmer(Slope ~ co_student_asking_for_info_ratio_w +
              (1 + co_student_asking_for_info_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```
  

```{r}
#Adding Individual Talkmove Predictors 32
model_32 <- blmer(Slope ~ co_student_making_claim_ratio_w +
              (1 + co_student_making_claim_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_33 <- blmer(Slope ~ co_student_providing_evidence_ratio_w +
              (1 + co_student_providing_evidence_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```


```{r}
# Display the model summary
tab_model(model_30, model_31, model_32, model_33,  dv.labels = c("Co Student Relating", "Co Student Asking for Info", "Co Student making claim", "Co Student providing evidence"))
```






### USING ROBUST MODEL: Talkmove by Co Student
```{r}
#Adding Individual Talkmove Predictors 30
model_304 <- rlmer(Slope ~ co_student_relating_ratio +
              (1 + co_student_relating_ratio | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 31
model_314 <- rlmer(Slope ~ co_student_asking_for_info_ratio +
              (1 + co_student_asking_for_info_ratio | tutor_ID),
              data = seda_mth, REML = FALSE)

```
  

```{r}
#Adding Individual Talkmove Predictors 32
model_324 <- rlmer(Slope ~ co_student_making_claim_ratio +
              (1 + co_student_making_claim_ratio | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_334 <- rlmer(Slope ~ co_student_providing_evidence_ratio +
              (1 + co_student_providing_evidence_ratio | tutor_ID),
              data = seda_mth, REML = FALSE)

```


```{r}
# Display the model summary
tab_model(model_304, model_314, model_324, model_334,  dv.labels = c("Co Student Relating", "Co Student Asking for Info", "Co Student making claim", "Co Student providing evidence"))
```











### Talkmove by Tutor
```{r}
#Adding Individual Talkmove Predictors 30
model_90 <- blmer(Slope ~ tutor_keeping_together_w   +
              (1 | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 31
model_91 <- blmer(Slope ~ tutor_students_relating_w   +
              (1  | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```
  
  
```{r}
#Adding Individual Talkmove Predictors 31
model_92 <- blmer(Slope ~ tutor_restating_w   +
              (1  | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```


```{r}
#Adding Individual Talkmove Predictors 32
model_93 <- blmer(Slope ~ tutor_revoicing_w  +
              (1  | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_94 <- blmer(Slope ~ tutor_reasoning_w  +
              (1  | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```


```{r}
# Display the model summary
tab_model(model_90, model_91, model_92, model_93, model_94,  dv.labels = c("Tutor Keeping Together", "Tutor Students Relating", "Tutor Restating", "Tutor Revoicing", "Tutor Reasoning"))
```











### RUNING USING ROBUST MODEL Talkmove by Tutor
```{r}
#Adding Individual Talkmove Predictors 30
model_2390 <- rlmer(Slope ~ tutor_keeping_together   +
              (1 | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 31
model_2391 <- rlmer(Slope ~ tutor_students_relating   +
              (1  | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```
  
  
```{r}
#Adding Individual Talkmove Predictors 31
model_2392 <- rlmer(Slope ~ tutor_restating   +
              (1  | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```


```{r}
#Adding Individual Talkmove Predictors 32
model_2393 <- rlmer(Slope ~ tutor_revoicing  +
              (1  | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_2394 <- rlmer(Slope ~ tutor_reasoning  +
              (1  | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```


```{r}
# Display the model summary
tab_model(model_2390, model_2391, model_2392, model_2393, model_2394,  dv.labels = c("Tutor Keeping Together", "Tutor Students Relating", "Tutor Restating", "Tutor Revoicing", "Tutor Reasoning"))
```




## Adding Intercept score as a predictor

### Talkmove by Student
```{r}
#Adding Individual Talkmove Predictors 30
model_302 <- blmer(Slope ~ Intercept + student_relating_ratio_w +
              (1 + Intercept + student_relating_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 31
model_312 <- blmer(Slope ~ Intercept + student_asking_for_info_ratio_w +
              (1 + Intercept + student_asking_for_info_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```
  

```{r}
#Adding Individual Talkmove Predictors 32
model_322 <- blmer(Slope ~ Intercept + student_making_claim_ratio_w +
              (1 + Intercept + student_making_claim_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_332 <- blmer(Slope ~ Intercept + student_providing_evidence_ratio_w +
              (1 + Intercept + student_providing_evidence_ratio_w | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```


```{r}
# Display the model summary
tab_model(model_302, model_312, model_322, model_332,  dv.labels = c("Student Relating", "Student Asking for Info", "Student making claim", "Student providing evidence"))
```




## Other models
```{r}
model2112 <- blmer(Slope ~ student_talkmove_ratio_w + co_student_talkmove_ratio_w + tutor_talkmove_ratio_w  + tutor_utterance_ratio_w + Intercept + (1  | tutor_ID), data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))


model2912 <- blmer(Slope ~ student_talkmove_ratio_w + co_student_talkmove_ratio_w + tutor_talkmove_ratio_w  + student_utterance_ratio_w + co_student_utterance_ratio_w + Intercept + (1  | tutor_ID), data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

tab_model(model2112, model2912)

```





## Other models with roboust model
```{r}
model21120 <- rlmer(Slope ~ student_talkmove_ratio + co_student_talkmove_ratio + tutor_talkmove_ratio  + tutor_utterance_ratio + Intercept + (1  | tutor_ID), data = seda_mth, REML = FALSE)


model29120 <- rlmer(Slope ~ student_talkmove_ratio + co_student_talkmove_ratio + tutor_talkmove_ratio  + student_utterance_ratio + co_student_utterance_ratio + Intercept + (1  | tutor_ID), data = seda_mth, REML = FALSE)

tab_model(model21120, model29120)

```







## Interaction of student and co_student on individual talkmove labels
```{r}
#Adding Individual Talkmove Predictors 30
model_301 <- blmer(Slope ~ student_relating_ratio_w*co_student_relating_ratio_w + tutor_utterance_ratio_w +
              (1 | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 31
model_311 <- blmer(Slope ~ student_asking_for_info_ratio_w*co_student_asking_for_info_ratio_w + tutor_utterance_ratio_w +
              (1 | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```
  

```{r}
#Adding Individual Talkmove Predictors 32
model_321 <- blmer(Slope ~ student_making_claim_ratio_w*co_student_making_claim_ratio_w + tutor_utterance_ratio_w +
              (1 | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```

```{r}
#Adding Individual Talkmove Predictors 32
model_331 <- blmer(Slope ~ student_providing_evidence_ratio_w*co_student_providing_evidence_ratio_w +
              (1 | tutor_ID),
              data = seda_mth, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

```


```{r}
# Display the model summary
tab_model(model_301, model_311, model_321, model_331,  dv.labels = c("Student Relating", "Student Asking for Info", "Student making claim", "Student providing evidence"))
```



# Interaction Effects from Sidney
```{r}
data <- seda_mth;
data$student_talkmove_ratioWZ <- scale(DescTools::Winsorize(data$unweighted_student_talkmove_ratio,                                                   quantile(data$unweighted_student_talkmove_ratio, probs = c(0, 0.99), na.rm = TRUE)))
data$co_student_talkmove_ratioWZ <- scale(DescTools::Winsorize(data$unweighted_co_student_talkmove_ratio,  quantile(data$unweighted_co_student_talkmove_ratio, probs = c(0, .99), na.rm = T)))
data$tutor_talkmove_ratioWZ <- scale(DescTools::Winsorize(data$unweighted_tutor_talkmove_ratio,  quantile(data$unweighted_tutor_talkmove_ratio, probs = c(0, .99), na.rm = T)))
data$tutor_utterance_ratioWZ <- scale(DescTools::Winsorize(data$unweighted_tutor_utterance_ratio,  quantile(data$unweighted_tutor_utterance_ratio, probs = c(0, .99), na.rm = T)))
data$tutor_talkmove_ratioZ <- scale(data$unweighted_tutor_talkmove_ratio)

hist(data$student_talkmove_ratioWZ)
hist(data$co_student_talkmove_ratioWZ)
hist(data$tutor_talkmove_ratioWZ)
hist(data$tutor_utterance_ratioWZ)


m <- lmer(Slope ~ student_talkmove_ratioWZ*co_student_talkmove_ratioWZ + student_talkmove_ratioWZ *tutor_talkmove_ratioWZ + tutor_utterance_ratioWZ + (1| tutor_ID), data = data, control = lmerControl(optimizer = "bobyqa"))

Anova(m, type = 3)
tab_model(m)

visreg::visreg(m, "student_talkmove_ratioWZ", by = "co_student_talkmove_ratioWZ", gg = T, breaks = c(-1, 0, 1))

Mod_list <- list(co_student_talkmove_ratioWZ = c(-1, 0, 1))

emtrends(m, ~student_talkmove_ratioWZ*co_student_talkmove_ratioWZ, var="student_talkmove_ratioWZ",at=Mod_list)

```
