---
title: "Student Engagmement"
author: "Kelechi Ezema"
date: "`r Sys.Date()`"
output: 
  html_document:
    number_sections: true
knit: (function(inputFile, encoding) { 
          rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file= "Team_engagment_april2nd.html") })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r message=FALSE, warning=FALSE}
# load packages #####
library(tidyverse)  # data processing
library(haven)      # read in stata data
library(vtable)     # summary tables
library(labelled)   # to see and create variable labels
library(lme4)      # estimate MLM
library(sjPlot)    # regression tables
library(lmerTest)  # hypothesis testing for MLM
library(quantreg)
library(blme)
library(writexl)
library(openxlsx)
library(robustlmm)
library(DescTools)
library(reshape2)
library(robustlmm)
library(visreg)
library(emmeans)
library(car)

```


## Load Data

```{r}


# student_tutor_file <- read.csv(file = "student_tutor_ready_for_rcode_april_22_asr_augumened_with_confidence.csv")
# student_tutor_file <- read.csv(file = "student_tutor_ready_for_rcode_april_21_asr_augumened.csv")
student_tutor_file <- read.csv(file = "student_tutor_ready_for_rcode_april_22_asr_fine_tuned.csv")



```


## Self reported engagement
```{r}
data <- student_tutor_file

data$mid_year_math_relationship_average_rating <- as.numeric(data$mid_year_math_relationship_average_rating)

data$student_id <- data$Anon.Student.ID;
data$tutor_id <- data$Fellow.ID;

begin_vars <- colnames(student_tutor_file)[34:38];
mid_vars <- colnames(student_tutor_file)[39:44];
end_vars <- colnames(student_tutor_file)[45:50];


psych::alpha(data[begin_vars], na.rm = T)
psych::alpha(data[mid_vars], na.rm = T)
psych::alpha(data[end_vars], na.rm = T)

data$begin <- rowMeans(data[begin_vars], na.rm = T)
data$mid <- rowMeans(data[mid_vars], na.rm = T)
data$end <- rowMeans(data[end_vars], na.rm = T)


vars <- c("begin", "mid", "end");
psych::alpha(data[vars], na.rm = T)

data$engagement <- rowMeans(data[vars], na.rm = T)

tableone::CreateContTable(vars = vars, data = data);

data.melt <- melt(data[c(vars, "student_id", "tutor_id")], id = c("student_id", "tutor_id"))

m <- lmer(value ~ variable + (1 | student_id:tutor_id) + (1|tutor_id), data = data.melt)
tab_model(m)

emmeans::emmeans(m, pairwise ~ variable)

```




## Data Filterering

```{r}
student_tutor_data <- data


# #Select Student_Tutor_Group with tutor in the session
# student_tutor_data <- student_tutor_data %>% filter(is.na(utterance_proportion_tutor) == FALSE)


# Select Student_Tutor_Group with unique_session_IDs_count > 10
student_tutor_data <- student_tutor_data %>% filter(unique_session_IDs_count >= 10)

#Select Student_Tutor_Group with achievement score
student_tutor_data <- student_tutor_data %>% filter(is.na(I) == FALSE)


dim(student_tutor_data)
```

## Column Renaming

```{r}
student_tutor_data <- student_tutor_data %>%
  mutate(
         student_tm_mean = talkmove_proportion_mean,
         student_utterance_mean = utterance_proportion_mean,
         student_word_mean = words_proportion_mean,
         
         
         co_student_tm_mean = co_student_talkmove_proportion_mean,
         co_student_utterance_mean = co_student_utterance_proportion_mean,
         co_student_word_mean = co_student_words_proportion_mean,
         
         tutor_tm_mean = tutor_talkmove_proportion_mean,
         tutor_utterance_mean = tutor_utterance_proportion_mean,
         tutor_word_mean = tutor_words_proportion_mean,


         Intercept = I,
         Slope = S,
         num_sessions = unique_session_IDs_count,
  )

```


<!-- ## Averaging Student Group Slopes (Only used in Section 11.2) -->
<!-- ```{r} -->
<!-- #Group by student_tutor_group, calculate group_slope, -->
<!-- student_tutor_data <- student_tutor_data %>% -->
<!--   mutate(S = as.numeric(S), -->
<!--        I = as.numeric(I), -->
<!--        num_sessions = as.numeric(num_sessions)) %>% -->
<!--  group_by(student_tutor_group) %>% -->
<!--  mutate(group_slope = mean(S, na.rm = TRUE), -->
<!--         group_intercept = mean(I, na.rm = TRUE), -->
<!--         group_engagement = mean(engagement, na.rm = TRUE),  -->
<!--         num_sessions_mean = mean(num_sessions, na.rm = TRUE), -->
<!--         ) %>% -->
<!--  ungroup() -->


<!-- # Create student_ID and tutor_ID from student_tutor_id -->
<!-- student_tutor_data <- student_tutor_data %>% -->
<!--   mutate(student_tutor_id = as.character(student_tutor_id)) %>% -->
<!--   separate(student_tutor_id, into = c("student_ID", "tutor_ID"), sep = "_", remove = FALSE) %>% -->
<!--   mutate(student_ID = as.numeric(student_ID), -->
<!--          tutor_ID = as.numeric(tutor_ID)) -->

<!-- ``` -->





## Rescaling Achievement Intercept and Slope

```{r}
student_tutor_data <- student_tutor_data %>%
  mutate(
         Slope = Slope *100,
         Intercept = Intercept*100
  )

```



## Histogram for predictors before winsorization
```{r}
plot_histogram <- function(df, vars, id)
{
  data.plot <- melt(df[c(id, vars)],  id = id);
  ggplot(data.plot, aes(x = value)) + geom_histogram() + facet_wrap(~variable, scales = "free")
}


vars <- c("student_tm_mean", "student_utterance_mean", "student_word_mean", 
          "co_student_tm_mean", "co_student_utterance_mean", "co_student_word_mean",
          "tutor_tm_mean", "tutor_utterance_mean", "tutor_word_mean", "num_sessions")

plot_histogram(student_tutor_data, vars, id = "student_tutor_id")


```


## Winzeration and normalization of Predictor variables
```{r}
#Winsorize the variables

vars <- c("student_tm_mean", "student_utterance_mean", "student_word_mean",  
         "co_student_tm_mean", "co_student_utterance_mean", "co_student_word_mean",
         "tutor_tm_mean", "tutor_utterance_mean", "tutor_word_mean", "num_sessions")

for (var in vars) {
  student_tutor_data[paste0(var, "_ZW")] <- scale(DescTools::Winsorize(student_tutor_data[[var]], quantile(student_tutor_data[[var]], probs=c(0.0, 0.99), na.rm = FALSE)))
}
```




<!-- ## Cummulate Frequency Table of data   -->
<!-- ```{r} -->

<!-- freq_table <- function(x) -->
<!-- { -->
<!--   return(cbind(Freq=table(x), Cumul=cumsum(prop.table(table(x))), relative=prop.table(table(x)))); -->
<!-- } -->

<!-- # Print the frequency table in 2 decimal places -->
<!-- freq_table(round(student_tutor_data$num_sessions_ZW, 1) ) -->


<!-- ``` -->


## Histogram for predictors after winsorization
```{r}
#Histogram for all the predictors
vars <- c("student_tm_mean_ZW", "student_utterance_mean_ZW", "student_word_mean_ZW", 
          "co_student_tm_mean_ZW", "co_student_utterance_mean_ZW", "co_student_word_mean_ZW",
          "tutor_tm_mean_ZW", "tutor_utterance_mean_ZW", "tutor_word_mean_ZW", "num_sessions_ZW")

plot_histogram(student_tutor_data, vars, id = "student_tutor_id")


```


## Corrlation of independent variables 

```{r}
# Select relevant variables
data <- student_tutor_data[, c("student_tm_mean_ZW",  "student_utterance_mean_ZW", "student_word_mean_ZW", 
                      "co_student_tm_mean_ZW", "co_student_utterance_mean_ZW", "co_student_word_mean_ZW",
                      "tutor_tm_mean_ZW", "tutor_utterance_mean_ZW", "tutor_word_mean_ZW", "num_sessions_ZW")]  

#Calculate a correlation matrix
cor_matrix <- cor(data)

tab_corr(data)
```

## MLM Modeling



### Slope ~ student_tm_mean
```{r}
model_01 <- blmer(Slope ~ student_tm_mean_ZW + co_student_tm_mean_ZW + tutor_tm_mean_ZW + tutor_utterance_mean_ZW + num_sessions_ZW +
              (1 | tutor_ID),
              data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))


tab_model(model_01)

# check for multicollinearity
vif(model_01)
```


### Slope ~ student_tm_mean*co_student_tm_mean

```{r}
model_02 <- blmer(Slope ~ student_tm_mean_ZW*co_student_tm_mean_ZW + student_tm_mean_ZW*tutor_tm_mean_ZW + tutor_utterance_mean_ZW + num_sessions_ZW +
              (1 | tutor_ID),
              data = student_tutor_data, REML = TRUE, control = lmerControl(optimizer = "bobyqa"))


tab_model(model_02)

# check for multicollinearity
vif(model_02)
```

